---
title: "1a: Clean SB + ELFK (LA + NYC cohorts) Data"
author: "Paul A. Bloom"
date: "April 22, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown cleans the LA (SB) and NYC (ELFK) cohort GI and anxiety symptoms data. Files are pulled from the rawData directory and output to the cleanData directory. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Tidyverse
```{r, message=FALSE, warning=FALSE, results='hide'}


library(tidyverse)
library(VIM)


# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

# Make file structure
```{r}
system('mkdir ../cleanData') # to output the clean data
system('mkdir ../plots') # to output results from subsequent analysis scripts
system('mkdir ../models') # to output results from subsequent analysis scripts
system('mkdir ../output') # to output results from subsequent analysis scripts
```


# Clean up SB Data


## Pull in SB dataframes, initial cleaning
```{r SB init cleaning}
# Pull in GI data GI symptoms, adoption, sex, age (but we won't use this age because it is rounded)
SBdata = read.csv("../rawData/GIANXSx_SB.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(starts_with('GI_Baseline'), SUBID, bl_age_gi_new, International_adoption, Sex) %>%
  # Compute the CBCL GI sum score by summing GI individual items for each subject:
  mutate(CBCL_GI_sum = rowSums(cbind(GI_Baseline_nausea, GI_Baseline_stom_cramps, GI_Baseline_vomit, GI_Baseline_constip))) %>%
  # simply rename the GI individual items now, to drop the prefix GI_Baseline:
  rename_at(vars(starts_with("GI_Baseline_")), ~case_when(
    grepl("nausea", .) ~ "nausea",
    grepl("stom_cramps", .) ~ "stomachache_cramps",
    grepl("constip", .) ~ "constipated",
    grepl("vomit", .) ~  "vomiting"
  )) %>%
  # Exclude outliers:
  filter(CBCL_GI_sum <= 10)

# Pull in SB master for non-rounded ages
sbMaster = read.csv('../rawData/sbMaster.csv', stringsAsFactors = FALSE)
sbMasterLong = sbMaster %>%
  # convert the data to long format, one row for each subject X timepoint (wave)
  tidyr::gather(key = 'wave', value = 'age', contains('SUBAGE_Session')) %>%
  # create a new column (in long format) to indicate the wave that each row corresponds to
  mutate(name = case_when(
    wave == 'SUBAGE_Session1' ~  paste0(IDENT_SUBID, '_pre'),
    wave == 'SUBAGE_session2' ~  paste0(IDENT_SUBID),
    wave == 'SUBAGE_session3' ~ paste0(IDENT_SUBID, '_fu1'),
    wave == 'SUBAGE_session4' ~ paste0(IDENT_SUBID, '_fu2')
  ),
  # also convert the age into years
  ageYrs = age/12) %>%
  # finally, filter by subjects who have age data entered
  dplyr::filter(!is.na(ageYrs)) 

# Get SCARED individual items
sbScaredIndiv = read.csv('../rawData/SB_scared_individual_items.csv', 
                         stringsAsFactors = FALSE) %>%
   dplyr::select(-sum_scared)

```

## Clean SCARED SB data, imputing where necessary
```{r SB Imputing, message=FALSE, warning=FALSE}
# Count how many NAs are in each row (by subject)
sbScaredIndiv$na_count <- apply(sbScaredIndiv, 1, function(x) sum(is.na(x)))

# impute for people with missing (but 20 or fewer items missing) using 5-nn imputation
sbScaredIndiv = sbScaredIndiv %>%
  dplyr::filter(na_count <= 20) %>%
  dplyr::select(-na_count) %>% # now discard the na_count column
  VIM::kNN(data = ., k = 5, imp_var = FALSE) 

# take sum of SCARED across rows
sbScaredIndiv$sum_scared = rowSums(select(sbScaredIndiv, starts_with('SCARED')))

# select just the sum score, and create the binarized threshold (1 = participants at or over clinical threshold of 25, 0 = below threshold)
sbScaredIndiv = sbScaredIndiv %>% 
  dplyr::select(SUBID, sum_scared) %>%
  mutate(scaredBin = ifelse(sum_scared >= 25, 1, 0))


```

## Correct SB ages in this chunk
```{r correcting SB ages}
# Previously, ages had been rounded down to the nearest year
# Now we pull in the exact ages from the SB master, and match the exact age where the rounding happened
sbMasterGrouped = sbMasterLong %>%
  group_by(IDENT_SUBID) %>%
  # create a new column for the age at each wave (timepoint):
  summarise(n=n(), firstAge=ageYrs[1], secondAge=ageYrs[2], thirdAge=ageYrs[3], fourthAge=ageYrs[4]) %>%
  # find the floor and nearest integer of the above ages:
  mutate_at(vars(contains("Age",ignore.case = F)), .funs = list("Floor"=floor, "Round"=round)) %>%
  # remove the underscore from the auto-generated variable names:
  rename_at(vars(contains("Floor"), contains("Round")), ~sub("_", "", .)) %>%
  # select resultant variables; merge with the outcome and predictor variables by subject:
  dplyr::select(SUBID = IDENT_SUBID, n, contains("Age", ignore.case = F)) %>%
  left_join(SBdata, by = "SUBID")


# Correct the SB ages since they were just integers before,as follows:
## 1. If the age matches an age rounded down, use the age from that wave
## 2. If not, it should match a rounded age (to NEAREST integer) from that wave
ageCorrectedSB = sbMasterGrouped %>%
  dplyr::filter(!is.na(bl_age_gi_new)) %>%
  dplyr::group_by(SUBID) %>%
  # first flag rows in which a match occurs with the floored age:
  mutate(matchFloor = ifelse(bl_age_gi_new %in% c(firstAgeFloor, secondAgeFloor, thirdAgeFloor, fourthAgeFloor), 1, 0),
         # also flag rows in which a match occurs with the roundeded age:
         matchRound = ifelse(bl_age_gi_new %in% c(firstAgeRound, secondAgeRound, thirdAgeRound, fourthAgeRound), 1, 0),
         # now use whichever match occurred as the correct "ageCorrect":
         ageCorrect = case_when(
           matchFloor == 1 & bl_age_gi_new == firstAgeFloor ~ firstAge,
           matchFloor == 1 & bl_age_gi_new == secondAgeFloor ~ secondAge,
           matchFloor == 1 & bl_age_gi_new == thirdAgeFloor ~ thirdAge,
           matchFloor == 1 & bl_age_gi_new == fourthAgeFloor ~ fourthAge,
           matchRound == 1 & bl_age_gi_new == firstAgeRound ~ firstAge,
           matchRound == 1 & bl_age_gi_new == secondAgeRound ~ secondAge,
           matchRound == 1 & bl_age_gi_new == thirdAgeRound ~ thirdAge,
           matchRound == 1 & bl_age_gi_new == fourthAgeRound ~ fourthAge,
            # a few need to be hard coded by taking the earliest age:
           SUBID %in% c('SB024', 'SB073', 'SB074', 'SB092', 'SB164', 'SB252', 'SB270', 'SB289', 'SB319', 'SB372') ~ firstAge
  )) %>% # close the case_when() and the mutate()
  # delete the age variables used as intermediary matching criteria:
  dplyr::select(., -contains('Floor'), -contains('Round'), -firstAge, -secondAge, -thirdAge, -fourthAge, -bl_age_gi_new) %>%
  # rename our age variable; and de-select desired columns:
  select(bl_age_gi_new = ageCorrect, everything(), -n)
```

## For SB, join GI/demogs data with SCARED, write cleaned data to CSV
```{r, warning=FALSE}
# Join the two frames and drop NA values
sb = left_join(sbScaredIndiv, ageCorrectedSB) %>%
  drop_na(CBCL_GI_sum, bl_age_gi_new, Sex, International_adoption) 


# write to clean csv folder
write.csv(sb, file = '../cleanData/sbDataClean.csv', row.names = FALSE)
```

# Clean up ELFK Data

```{r}
# Read in data
ELFKcbcl = read.csv("../rawData/CBCL_ELFK.csv", stringsAsFactors = FALSE)
ELFKscared = read.csv("../rawData/SCARED_ELFK.csv", stringsAsFactors = FALSE)
ELFKdemo = read.csv("../rawData/ELFK_demo.csv", stringsAsFactors = FALSE)

#Average the ELFK SCARED values
ELFKscared$time1_scared_11removed_average = rowMeans(dplyr::select(ELFKscared, starts_with('SCARED')))
ELFKscared$sum_scared = rowSums(select(ELFKscared, starts_with('SCARED')))

#merge the two dfs based on SUBID
elfk  = left_join(ELFKcbcl, ELFKscared, by="SUBID") %>%
  left_join(ELFKdemo, by = "SUBID") %>%
  mutate(CBCL_GI_sum = nausea + stomachache_cramps + vomiting + constipated)


#make predictor variable + clean
elfk = elfk %>%
  # compute the CBCL GI sum scores:
  mutate(CBCL_GI_sum = nausea + stomachache_cramps + vomiting + constipated,
         # create a binary factor indicating if a subject was internationally adopted:
         International_adoption = ifelse(group == 0, 0, 1)) %>%
  # Select and rename varables as needed
  dplyr::select(SUBID, CBCL_GI_sum,
                # the raw GI items:
                nausea, stomachache_cramps, vomiting, constipated, 
                # rename age and sex for later merging with other data frames:
                bl_age_gi_new = age, Sex = sex, 
                # computed variables:
                time1_scared_11removed_average, International_adoption, sum_scared) %>%
  # drop NAs by selected columns:
  drop_na(CBCL_GI_sum, bl_age_gi_new, Sex, International_adoption, time1_scared_11removed_average) %>%
  # finally, apply thresholding to the scared suum scores to create scaredBin (as above):
  mutate(scaredBin = ifelse(sum_scared >= 25, 1, 0))
  
# write to clean csv folder
write.csv(elfk, file = '../cleanData/elfkDataClean.csv', row.names = FALSE)
```

# Session Info
```{r}
sessionInfo()
```
