---
title: "1a: Clean SB + ELFK (LA + NYC cohorts) Data"
author: "Paul A. Bloom"
date: "April 22, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown cleans the LA (SB) and NYC (ELFK) cohort GI and anxiety symptoms data. Files are pulled from the rawData directory and output to the cleanData directory. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Tidyverse
```{r,message=FALSE, warning=FALSE}
library(tidyverse)
library(VIM)
```


# Clean up SB Data


## Pull in SB dataframes, initial cleaning
```{r SB init cleaning}
# Pull in GI data GI symptoms, adoption, sex, age (but we won't use this age because it is rounded)
SBdata = read.csv("../rawData/GIANXSx_SB.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(., starts_with('GI_Baseline'), SUBID, bl_age_gi_new, International_adoption, Sex) %>%
  mutate(., CBCL_GI_sum = GI_Baseline_nausea + GI_Baseline_stom_cramps + GI_Baseline_vomit + GI_Baseline_constip,
         nausea = GI_Baseline_nausea, 
                stomachache_cramps = GI_Baseline_stom_cramps, 
                constipated = GI_Baseline_constip, 
                vomiting = GI_Baseline_vomit) %>%
  filter(., CBCL_GI_sum <=10) %>% # Exclude outliers
  dplyr::select(., -GI_Baseline_nausea, -GI_Baseline_stom_cramps, -GI_Baseline_constip, -GI_Baseline_vomit)

# Pull in SB master for non-rounded ages
sbMaster = read.csv('../rawData/sbMaster.csv', stringsAsFactors = FALSE)
sbMasterLong = sbMaster %>%
  tidyr::gather(., key = 'wave', value = 'age', contains('SUBAGE_Session')) %>%
  mutate(name = case_when(
    wave == 'SUBAGE_Session1' ~  paste0(IDENT_SUBID, '_pre'),
    wave == 'SUBAGE_session2' ~  paste0(IDENT_SUBID),
    wave == 'SUBAGE_session3' ~ paste0(IDENT_SUBID, '_fu1'),
    wave == 'SUBAGE_session4' ~ paste0(IDENT_SUBID, '_fu2')
  ),
  ageYrs = age/12) %>%
  dplyr::filter(., !is.na(ageYrs)) 

# Get SCARED sums
sbScaredIndiv = read.csv('../rawData/SB_scared_individual_items.csv', stringsAsFactors = FALSE) %>%
   dplyr::select(., -sum_scared)

```

## Clean SCARED SB data, imputing where needed
```{r SB Imputing, message=FALSE, warning=FALSE}
# Count how many NAs  
sbScaredIndiv$na_count <- apply(sbScaredIndiv, 1, function(x) sum(is.na(x)))

# impute for people with missing (but less than 20 items missing) using 5-nn imputation
sbScaredIndiv = sbScaredIndiv %>%
  dplyr::filter(., na_count <= 20) %>%
  dplyr::select(., -na_count) %>%
  VIM::kNN(., k = 5, imp_var = FALSE) 

# take sum of SCARED across rows
sbScaredIndiv$sum_scared = rowSums(select(sbScaredIndiv, starts_with('SCARED')))

# select just the sum score, and create the binarized threshold (1 = participants at or over clinical threshold of 25, 0 = below threshold)
sbScaredIndiv = sbScaredIndiv %>% 
  dplyr::select(., SUBID, sum_scared) %>%
  mutate(scaredBin = ifelse(sum_scared >= 25, 1, 0))


```

## Correct SB ages in this chunk
```{r}
# Previously, ages had been rounded down to the nearest year
# Now we pull in the exact ages from the SB master, and match the exact age where the rounding happened
sbMasterGrouped = sbMasterLong %>%
  group_by(IDENT_SUBID) %>%
  summarise(n = n(), 
            firstAge = ageYrs[1], secondAge = ageYrs[2], thirdAge = ageYrs[3], fourthAge = ageYrs[4],
            firstAgeFloor = floor(ageYrs[1]), secondAgeFloor = floor(ageYrs[2]), thirdAgeFloor = floor(ageYrs[3]), fourthAgeFloor = floor(ageYrs[4]),
            firstAgeRound = round(ageYrs[1]), secondAgeRound = round(ageYrs[2]), thirdAgeRound = round(ageYrs[3]), fourthAgeRound = round(ageYrs[4])) %>%
  dplyr::select(., SUBID = IDENT_SUBID, n, firstAge, secondAge, thirdAge, fourthAge, contains('Floor'), contains('Round')) %>%
  left_join(SBdata)


# Correct the SB ages since they were just integers before:
# If the age matches an age rounded down, use the age from that wave
# If not, it should match a rounded age (to NEAREST integer) from that wave
ageCorrectedSB = sbMasterGrouped %>%
  dplyr::filter(., !is.na(bl_age_gi_new)) %>%
  dplyr::group_by(SUBID) %>%
  mutate(matchFloor = ifelse(bl_age_gi_new %in% c(firstAgeFloor, secondAgeFloor, thirdAgeFloor, fourthAgeFloor), 1, 0),
         matchRound = ifelse(bl_age_gi_new %in% c(firstAgeRound, secondAgeRound, thirdAgeRound, fourthAgeRound), 1, 0),
         ageCorrect = case_when(
           matchFloor == 1 & bl_age_gi_new == firstAgeFloor ~ firstAge,
           matchFloor == 1 & bl_age_gi_new == secondAgeFloor ~ secondAge,
           matchFloor == 1 & bl_age_gi_new == thirdAgeFloor ~ thirdAge,
           matchFloor == 1 & bl_age_gi_new == fourthAgeFloor ~ fourthAge,
           matchRound == 1 & bl_age_gi_new == firstAgeRound ~ firstAge,
           matchRound == 1 & bl_age_gi_new == secondAgeRound ~ secondAge,
           matchRound == 1 & bl_age_gi_new == thirdAgeRound ~ thirdAge,
           matchRound == 1 & bl_age_gi_new == fourthAgeRound ~ fourthAge,
           SUBID %in% c('SB024', 'SB073', 'SB074', 'SB092', 'SB164', 'SB252', 'SB270', 'SB289', 'SB319', 'SB372') ~ firstAge # a few need to be hard coded
         )) %>%
  dplyr::select(., -contains('Floor'), -contains('Round'), -firstAge, -secondAge, -thirdAge, -fourthAge) %>%
  mutate(., bl_age_gi_new = ageCorrect) %>%
  dplyr::select(., -ageCorrect, -n)

```

## For SB, join GI/demogs data with SCARED, write cleaned data to CSV
```{r}
# Join the two frames and drop NA values
sb = left_join(sbScaredIndiv, ageCorrectedSB) %>%
  drop_na(., CBCL_GI_sum, bl_age_gi_new, Sex, International_adoption) 


# write to clean csv folder
write.csv(sb, file = '../cleanData/sbDataClean.csv', row.names = FALSE)
```

# Clean up ELFK Data

```{r}
# Read in data
ELFKcbcl = read.csv("../rawData/CBCL_ELFK.csv", stringsAsFactors = FALSE)
ELFKscared = read.csv("../rawData/SCARED_ELFK.csv", stringsAsFactors = FALSE)
ELFKdemo = read.csv("../rawData/ELFK_demo.csv", stringsAsFactors = FALSE)

#Average the ELFK SCARED values
ELFKscared$time1_scared_11removed_average = rowMeans(dplyr::select(ELFKscared, starts_with('SCARED')))
ELFKscared$sum_scared = rowSums(select(ELFKscared, starts_with('SCARED')))

#merge the two dfs based on SUBID
elfk  = left_join(ELFKcbcl, ELFKscared, by="SUBID") %>%
  left_join(., ELFKdemo, by = "SUBID") %>%
  mutate(., CBCL_GI_sum = nausea + stomachache_cramps + vomiting + constipated)


#make predictor variable + clean
elfk = elfk %>%
  mutate(., CBCL_GI_sum = nausea + stomachache_cramps + vomiting + constipated,
         International_adoption = ifelse(group == 0, 0, 1)) %>%
  dplyr::select(., SUBID, CBCL_GI_sum, nausea, stomachache_cramps, vomiting, 
                constipated, bl_age_gi_new = age, Sex = sex, time1_scared_11removed_average, International_adoption, sum_scared) %>%
  drop_na(., CBCL_GI_sum, bl_age_gi_new, Sex, International_adoption, time1_scared_11removed_average) %>%
  mutate(scaredBin = ifelse(sum_scared >= 25, 1, 0))
  
# write to clean csv folder
write.csv(elfk, file = '../cleanData/elfkDataClean.csv', row.names = FALSE)
```

# Session Info
```{r}
sessionInfo()
```
