---
title: "1b: Clean the HBN KSADS data"
author: "Paul A. Bloom"
date: "August 5, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown takes in the raw HBN spreadsheet of clinician diagnoses (for all diagnoses) on the KSADS and outputs a cleaned set in tabular form, with rows as participants and columns as respective diagnoses. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
library(tidyverse)
```

# Clean the clinician-consensus evals

This dataset isn't structured in a way that is particularly helpful for futher analysis, so we pull out the 'ClinicianConsensus.DX_##' variables indicating up to 10 diagnoses that a given participant could have. Then, for every possible diagnosis of the 59 possible types, we loop through the data to create a binary indicator variable for each participant indicating if they have that diagnosis or not.

```{r}
# load in raw messy clinician consensus data
diagnoses = read.csv('../rawData/clinicianDiagnoses.csv', stringsAsFactors = FALSE)

# select the column for each diagnosis (up to 10 because of coding)
diagnoses= dplyr::select(diagnoses, Identifiers, 
                         Diagnosis_ClinicianConsensus.DX_01, 
                         Diagnosis_ClinicianConsensus.DX_02,
                         Diagnosis_ClinicianConsensus.DX_03,
                         Diagnosis_ClinicianConsensus.DX_04,
                         Diagnosis_ClinicianConsensus.DX_05,
                         Diagnosis_ClinicianConsensus.DX_06,
                         Diagnosis_ClinicianConsensus.DX_07,
                         Diagnosis_ClinicianConsensus.DX_08,
                         Diagnosis_ClinicianConsensus.DX_09,
                         Diagnosis_ClinicianConsensus.DX_10)

# find names of all possible diagnoses
possibleDiagnoses = unique(diagnoses$Diagnosis_ClinicianConsensus.DX_01)

# Remove blank space from vector of possible diagnoses
possibleDiagnoses = possibleDiagnoses[-47]

# Set up an output dataframe
diagFrame = setNames(data.frame(matrix(ncol = 59, nrow = 0)), possibleDiagnoses)

# For each possible diagnosis, mark if each subject has it or not
## Outer loop -- loops through participants
## Inner loop goes through each possible diagnosis (59)
for (row in 1:nrow(diagnoses)){
  diagFrame[row, 60] = diagnoses$Identifiers[row] # put participant identifier in column 60 of each row
  # for every other column, check if participant has that diagnosis. Yes = 1, no = 0
  for (column in 1:59){
    if (names(diagFrame)[column] %in% diagnoses[row,]){
      diagFrame[row,column] = 1
    }
    else{
      diagFrame[row, column] = 0
    }
  }
}

# pub subject identifiers back in
names(diagFrame)[60] = 'Identifiers'
write.csv(diagFrame, '../cleanData/clinicianConsensusDiagnoses.csv', row.names = FALSE)
```


# Session Info
```{r}
sessionInfo()
```

