---
title: "1c: HBN Data Cleaning and Splitting"
author: "Paul A. Bloom"
date: "April 22, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown cleans HBN data for the CBCL + SCARED and demographics, and also pulls in KSADS data previously cleaned for putting all together for analysis. The cleaning includes KNN imputation of missing survey items for participant with partial survey data, but NOT imputation of total measure scores for participants completely missing a measure. This markdown also splits the HBN data into a training set and test set

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Tidyverse
```{r, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(VIM)
library(caret)
source("helperFunctions.R")
theme_set(theme_bw())


# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

## Import Raw HBN Dataset
```{r}
raw = read.csv('../rawData/hbnRawData.csv', stringsAsFactors = FALSE)

# Make a key with just ID, age, and sex
# Sex: 0 = male, 1 = female
justId = raw %>%
  dplyr::select(Identifiers, age = Basic_Demos.Age, sex = Basic_Demos.Sex) %>%
  mutate(age = as.numeric(age))

```

## Clean CBCL items

We have to be careful here because some of the items are differently numbered in the preschool version (marked by 'pre' in the variable name) of the CBCL. A few participants have data on both the preschool and regular version of the CBCL, so we only use the preschool version if the regular version is missing. 
```{r}
# Select variables -- both preschool and older kid version of it
cbclItems = raw %>%
  # select and rename columns
  dplyr::select(Identifiers, 
                age = Basic_Demos.Age,
                nausea = CBCL.CBCL_56C,
                stomachache_cramps = CBCL.CBCL_56F, 
                vomiting = CBCL.CBCL_56G, 
                constipated = CBCL.CBCL_49, 
                nauseaPre = CBCL_Pre.CBCLpre_45, 
                stomachache_crampsPre = CBCL_Pre.CBCLpre_78, 
                vomitingPre = CBCL_Pre.CBCLpre_93, 
                constipatedPre = CBCL_Pre.CBCLpre_12) %>%
  # convert age to numeric
  mutate(age = as.numeric(age))


# Kids < 6 tend to have preschool version but not regular.
# If the preschool version data is present, and regular is missing fill in the items with that one
# Then get rid of extra preschool items
# Additionallly, compute the summed score
cbclItems = cbclItems %>%
  mutate(
    # nausea:
    nausea = as.numeric(ifelse((nausea == '.' & nauseaPre != '.'), nauseaPre, nausea)),
    # stomachache cramps:
    stomachache_cramps = as.numeric(
      ifelse((stomachache_cramps == '.' & stomachache_crampsPre != '.'), 
             stomachache_crampsPre, stomachache_cramps)),
    # vomiting
    vomiting = as.numeric(
      ifelse((vomiting == '.' & vomitingPre != '.'), 
             vomitingPre, vomiting)),
    # constipation:
    constipated = as.numeric(
      ifelse((constipated == '.' & constipatedPre != '.'), 
             constipatedPre, constipated))) %>%
  # delete preschool version following above recoding:
  dplyr::select(-contains('Pre')) %>%
  # compute sum score
  mutate(cbclGISum = nausea + stomachache_cramps + vomiting + constipated)

# Extract only complete data
# first with respect to NAs:
cbclComplete = cbclItems[complete.cases(cbclItems), ] %>%
  # and clear out rows with empty strings from the following variables as well:
  filter(
    nausea != '.', 
    stomachache_cramps != '.',
    vomiting != '.',
    constipated != '.',
    nausea != '', 
    stomachache_cramps != '',
    vomiting != '',
    constipated != ''
  )
```

## Clean scared parent items
```{r}
# select SCARED-P items
scaredParent = raw %>%
  dplyr::select(
    Identifiers, 
    contains('SCARED_P.SCARED_P_'), 
    -SCARED_P.SCARED_P_Total, 
    -SCARED_P.SCARED_P_SP, 
    -SCARED_P.SCARED_P_SH, 
    -SCARED_P.SCARED_P_SC, 
    -SCARED_P.SCARED_P_PN, 
    -SCARED_P.SCARED_P_GD,
    -SCARED_P.SCARED_P_11
  )

# Store participant identifiers temporarily 
idTemp = scaredParent$Identifiers

# remove ID variable, then make all data numeric (numbers are represented as strings in the raw data)
# Missing data represented with '.' -- will get turned to NA here
scaredParent = scaredParent %>%
  dplyr::select(-Identifiers) %>%
  mutate_if(is.character, as.numeric) 

# put IDs back in
scaredParent$Identifiers = idTemp

# Impute scared parent scores with partially complete data
scaredParentNotComplete = scaredParent

# see how many items each person is missing
scaredParentNotComplete$numMissing = rowSums(is.na(scaredParent))

# variables to use for imputation
impVarsParent = names(scaredParentNotComplete)[1:40]

# impute missing items for people missing only some items (5-NN imputation)
scaredParentPartial = scaredParentNotComplete %>%
  dplyr::filter(numMissing < 40) %>%
  # conduct imputation:
  VIM::kNN(data = ., k = 5, numFun = median, catFun = maxCat, 
           imp_var = TRUE, dist_var = impVarsParent, addRandom = FALSE)

# Save back into scaredParent (removing indicator varibales indicating for which participants imputation happened)
scaredParent = dplyr::select(scaredParentPartial, -contains('imp'))

# Get total SCARED-P sum score for each participant, take only complete cases, create binary indicator based on clinical cutoff threshold of >= 25, and remove item-level variables
scaredParent = scaredParent %>%
  mutate(scaredSumParent = rowSums(scaredParent[1:40], na.rm = TRUE)) %>%
  filter(complete.cases(.)) %>%
  mutate(scaredBinParent = ifelse(scaredSumParent >= 25, 1, 0)) %>%
  dplyr::select(Identifiers, scaredSumParent, scaredBinParent)
```

## Clean scared child items

The process is basically the same here as with SCARED-P
```{r}
# select SCARED-C items
scaredChild = raw %>%
  dplyr::select(
    Identifiers,contains('SCARED_SR.SCARED_SR_'), 
    -SCARED_SR.SCARED_SR_Total, 
    -SCARED_SR.SCARED_SR_SP, 
    -SCARED_SR.SCARED_SR_SH, 
    -SCARED_SR.SCARED_SR_SC, 
    -SCARED_SR.SCARED_SR_PN, 
    -SCARED_SR.SCARED_SR_GD,
    -SCARED_SR.SCARED_SR_11
  )

# Store participant identifiers temporarily 
idTempChild = scaredChild$Identifiers

# remove ID variable, then make all data numeric (numbers are represented as strings in the raw data)
# Missing data represented with '.' -- will get turned to NA here
scaredChild = scaredChild %>%
  dplyr::select(-Identifiers) %>%
  mutate_if(is.character, as.numeric) 

# put IDs back in
scaredChild$Identifiers = idTempChild

# Impute SCARED-C scores with partially complete data
scaredChildNotComplete = scaredChild

# see how many items each person is missing
scaredChildNotComplete$numMissing = rowSums(is.na(scaredChildNotComplete))

# variables to use for imputation (all individual items)
impVarsChild = names(scaredChildNotComplete)[1:40]

# impute missing items for people missing only some items
scaredChildPartial = scaredChildNotComplete %>%
  dplyr::filter(numMissing < 40) %>%
  # conduct imputation:
  VIM::kNN(data = ., k = 5, numFun = median, catFun = maxCat, 
           imp_var = TRUE, dist_var = impVarsChild, addRandom = FALSE) 

# Save back into scaredChild
scaredChild = dplyr::select(scaredChildPartial, -contains('imp'))

# Get total SCARED-C sum score for each participant, take only complete cases, create binary indicator based on clinical cutoff threshold of >= 25, and remove item-level variables
scaredChild = scaredChild %>%
  mutate(scaredSumChild = rowSums(scaredChild[1:40], na.rm = TRUE)) %>%
  filter(complete.cases(.)) %>%
  mutate(scaredBinChild = ifelse(scaredSumChild >= 25, 1, 0)) %>%
  dplyr::select(Identifiers, scaredSumChild, scaredBinChild) 
```


## KSADS

The data have already been mostly cleaned in 1b, but here we create a binary variable indicating a diagnosis of any one of 13 anxiety disorders. We also filter out subjects where the KSADS clinician evalution was marked as incomplete -- these participants will not be included in complete-cases analysis, and their KSADS diagnoses will be imputed for imputation pipelines.

```{r}
ksadsAllDiagnoses = read.csv('../cleanData/clinicianConsensusDiagnoses.csv', stringsAsFactors = FALSE) %>%
  dplyr::filter(No.Diagnosis.Given..Incomplete.Eval != 1) %>%
  # rename and select desired variables:
  dplyr::select(
    'Other Specified Anxiety Disorder' = Other.Specified.Anxiety.Disorder,
    'Social Anxiety / Social Phobia' = Social.Anxiety..Social.Phobia.,
    'Generalized Anxiety Disorder' = Generalized.Anxiety.Disorder,
    'Separation Anxiety'= Separation.Anxiety,
    'Unspecified Anxiety Disorder' = Unspecified.Anxiety.Disorder,
    'Specific Phobia' = Specific.Phobia, 
    'Obsessive Compulsive Disorder' = Obsessive.Compulsive.Disorder, 
    'Panic Disorder' = Panic.Disorder,
    'Adjustment Disorders' = Adjustment.Disorders, 
    'Acute Stress Disorder' = Acute.Stress.Disorder, 
    'Selective Mutism' = Selective.Mutism, 
    'Post-Traumatic Stress Disorder' = Posttraumatic.Stress.Disorder, 
    Agoraphobia, 
    Identifiers
  ) 

# Calculate sum across all rows (diagnoses)
ksadsAllDiagnoses$ksadsBin = ksadsAllDiagnoses %>%
  dplyr::select(-Identifiers) %>%
  rowSums()

# Binarize the ksadsBin variable to ask if participants had a diagnosis or not
ksads = ksadsAllDiagnoses %>%
  dplyr::select(ksadsBin, Identifiers) %>%
  mutate(ksadsBin = ifelse(ksadsBin > 0, 1, 0))
```

# Put complete dataset with missing values together
```{r}
# start with the identifiers key
justId %>%
  # remove one participant without age:
  filter(Identifiers != ',assessment', !is.na(age)) %>%
  # join the cbclItems to the key of identifiers/age etc:
  left_join(., cbclItems) %>%
  # join in the scared child items to the result:
  left_join(., scaredChild) %>%
  # join in the scared parent items to the result:
  left_join(., scaredParent) %>%
  # join in the ksads items to the result:
  left_join(., ksads) -> fullHBN # store final result as 'fullHBN'

# Remove participants with NO data for any measures
fullHBN = fullHBN %>%
  removeRowsAllNA(columns = 4:13) %>%
  # mean-center age
  mutate(ageCenter = age - mean(age))

# write out fullHBN
write.csv(fullHBN, file = '../cleanData/fullHBN.csv', row.names = FALSE)
```

## Calculate the number of missing data points
```{r}
# Calculate how many people are missing each measure
missingCBCL = nrow(filter(fullHBN, is.na(cbclGISum)))
missingScaredParent = nrow(filter(fullHBN, is.na(scaredSumParent)))
missingScaredChild = nrow(filter(fullHBN, is.na(scaredSumChild)))
missingKsads = nrow(filter(fullHBN, is.na(ksadsBin)))

# Make dataframes for different combinations of complete data
cbclAndAtLeastOneOutcome = fullHBN %>%
  # extract subjects with the CBCL and at least one SCARED outcome entered:
  filter(!is.na(cbclGISum), (!is.na(scaredSumParent | !is.na(scaredSumChild) | !is.na(ksadsBin))))

cbclAndScaredParent = fullHBN %>%
  # extract the subjects with the CBCL and the SCARED parent sum
  filter(!is.na(cbclGISum), !is.na(scaredSumParent))

cbclAndScaredChild = fullHBN %>%
  # extract the subjects with the CBCL and the SCARED child sum
  filter(!is.na(cbclGISum), !is.na(scaredSumChild))


cbclAndKsads = fullHBN %>%
  # extract the subjects with the CBCL and the binarized KSADS dx
  filter(!is.na(cbclGISum), !is.na(ksadsBin))

```

Missing:
  * CBCL: `r missingCBCL`
  * Scared Parent: `r missingScaredParent`
  * Scared Child: `r missingScaredChild`
  * Ksads: `r missingKsads`

# Partition out test set from data with cbcl and at least one outcome
```{r}
# set the seed so it is the same everytime
set.seed(112993)

# Split 75% of data for training, 25% for testing
trainCompleteIdx = caret::createDataPartition(cbclAndAtLeastOneOutcome$cbclGISum, p = .75)[[1]]
trainComplete = cbclAndAtLeastOneOutcome[trainCompleteIdx,]
testComplete = cbclAndAtLeastOneOutcome[-trainCompleteIdx,]

# Data for imputation is all data not included in the test set
trainForImpute = filter(fullHBN, !Identifiers %in% testComplete$Identifiers)
                                                
# Write out separate files for training/test -- commented out so we don't overwrite the random seeding
write.csv(trainComplete, file = '../cleanData/hbnTrainComplete.csv', row.names = FALSE) 
write.csv(testComplete, file = '../cleanData/hbnTestComplete.csv', row.names = FALSE)
write.csv(trainForImpute, file = '../cleanData/hbnTrainForImpute.csv', row.names = FALSE)
```


# Session Info
```{r}
sessionInfo()
```

