---
title: "1d: Impute Missing HBN Data"
author: "Paul A. Bloom"
date: "June 21, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown imputes missing items in the HBN data using 3NN and 9NN imputation (resulting in 2 different imputed datasets). Anxiety variables are imputed separately from CBCL GI items in efforts to avoid introducing artificial dependence between predictors and outcomes. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Load pacakages
```{r}
library(tidyverse)
library(VIM)
source("helperFunctions.R")
theme_set(theme_bw())


# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

## Load in HBN Training Set for Imputation
```{r}
hbnImpute = read.csv('../cleanData/hbnTrainForImpute.csv', stringsAsFactors = FALSE)

# Take out binary variables
dataForImputation = dplyr::select(hbnImpute, -scaredBinChild, -scaredBinParent, -cbclGISum)

# Define variables from which to impute predictors and outcomes (respectively)
imputationIV = dplyr::select(dataForImputation, -scaredSumChild, -scaredSumParent, -ksadsBin, -ageCenter)
imputationDV = dplyr::select(dataForImputation, -nausea, -stomachache_cramps, -vomiting, -constipated)
impVarsIV = names(imputationIV)[names(imputationIV) %in% c('age', 'sex')]
impVarsDV = names(imputationDV)[!names(imputationDV) %in% c('Identifiers', 'scaredSumChild')]
```

## Impute all missing variables using 3 and 9 nearest neighbors

  * Use the VIM package to impute the GI predictors and anxiety outcomes separately
  * Then bind back together, calculate sum scores

```{r}
# join an independent imputation of the IVs and the DVs
hbn3NNTrain =  left_join(
  kNN(imputationIV, k = 3, numFun = median, catFun = maxCat,
      imp_var = FALSE, dist_var = impVarsIV, addRandom = FALSE), 
  # impute the DV, wrapped in a select function to drop the age variable from the output before joining
  dplyr::select(kNN(imputationDV, k = 3, numFun = median, catFun = maxCat, 
                    imp_var = FALSE, dist_var = impVarsDV, addRandom = FALSE), 
                -age), # <-- deselect age and close the select()  
  # join the two results by the identifiers and gender:
  by = c('Identifiers', 'sex')) %>% # <-- close the left_join; pipe result into subsequent mutate()
  # compute further variables on the resultant imputed and merged data:
  mutate(scaredBinChild = ifelse(scaredSumChild >= 25, 1, 0),
         scaredBinParent = ifelse(scaredSumParent >= 25, 1, 0),
         cbclGISum = stomachache_cramps + vomiting + constipated + nausea)

# Repeat the above using a 9-nearest-neighbor imputation model
hbn9NNTrain = left_join(
  kNN(imputationIV, k = 9, numFun = median, catFun = maxCat, 
      imp_var = FALSE, dist_var = impVarsIV),
  dplyr::select(kNN(imputationDV, k = 9, numFun = median, catFun = maxCat, 
                    imp_var = FALSE, dist_var = impVarsDV, addRandom = FALSE), 
                -age), # <-- deselect age and close the select() 
  by = c('Identifiers', 'sex')) %>% # <-- close the left_join; pipe result into subsequent mutate()
  mutate(scaredBinChild = ifelse(scaredSumChild >= 25, 1, 0),
         scaredBinParent = ifelse(scaredSumParent >= 25, 1, 0),
         cbclGISum = stomachache_cramps + vomiting + constipated + nausea)

write.csv(hbn3NNTrain, file = '../cleanData/hbnTrain3NN.csv', row.names = FALSE)
write.csv(hbn9NNTrain, file = '../cleanData/hbnTrain9NN.csv', row.names = FALSE)
```

# Session Info
```{r}
sessionInfo()
```
