---
title: "1d: Impute Missing HBN Data"
author: "Paul A. Bloom"
date: "June 21, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown imputes missing items in the HBN data using 3NN and 9NN imputation (resulting in 2 different imputed datasets). Anxiety variables are imputed separately from CBCL GI items in efforts to avoid introducing artificial dependence between predictors and outcomes. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Load pacakages
```{r}
library(tidyverse)
library(VIM)
source('helperFunctions.R')
```

## Load in HBN Training Set for Imputation
```{r}
hbnImpute = read.csv('../cleanData/hbnTrainForImpute.csv', stringsAsFactors = FALSE)

# Take out binary variables
dataForImputation = dplyr::select(hbnImpute, -scaredBinChild, -scaredBinParent, -cbclGISum)

# Define variables from which to impute predictors and outcomes (respectively)
imputationIV = dplyr::select(dataForImputation, -scaredSumChild, -scaredSumParent, -ksadsBin, -ageCenter)
imputationDV = dplyr::select(dataForImputation, -nausea, -stomachache_cramps, -vomiting, -constipated)
impVarsIV = names(imputationIV)[names(imputationIV) %in% c('age', 'sex')]
impVarsDV = names(imputationDV)[!names(imputationDV) %in% c('Identifiers', 'scaredSumChild')]
```

## Impute all missing variables using 3 and 9 nearest neighbors

  * Use the VIM package to impute the GI predictors and anxiety outcomes separately
  * Then bind back together, calculate sum scores

```{r}
hbn3NNTrain =  kNN(imputationIV, k = 3, numFun = median, catFun = maxCat, imp_var = FALSE, dist_var = impVarsIV, addRandom = FALSE) %>%
  left_join(., dplyr::select(kNN(imputationDV, k = 3, numFun = median, catFun = maxCat, imp_var = FALSE, dist_var = impVarsDV, addRandom = FALSE), -age), by = c('Identifiers', 'sex')) %>%
  mutate(., scaredBinChild = ifelse(scaredSumChild >= 25, 1, 0),
         scaredBinParent = ifelse(scaredSumParent >= 25, 1, 0),
         cbclGISum = stomachache_cramps + vomiting + constipated + nausea)

hbn9NNTrain = kNN(imputationIV, k = 9, numFun = median, catFun = maxCat, imp_var = FALSE, dist_var = impVarsIV) %>%
  left_join(., dplyr::select(kNN(imputationDV, k = 9, numFun = median, catFun = maxCat, imp_var = FALSE, dist_var = impVarsDV, addRandom = FALSE), -age), by = c('Identifiers', 'sex')) %>%
  mutate(., scaredBinChild = ifelse(scaredSumChild >= 25, 1, 0),
         scaredBinParent = ifelse(scaredSumParent >= 25, 1, 0),
         cbclGISum = stomachache_cramps + vomiting + constipated + nausea)

write.csv(hbn3NNTrain, file = '../cleanData/hbnTrain3NN.csv', row.names = FALSE)
write.csv(hbn9NNTrain, file = '../cleanData/hbnTrain9NN.csv', row.names = FALSE)
```

# Session Info
```{r}
sessionInfo()
```
