---
title: "2a: Replicating GI-Anxiety Associations Across Cohorts"
author: "Paul A. Bloom"
date: "June 21, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```


This markdown runs the same linear/logistic regressions in the HBN (training data), LA, and NYC cohorts predicting SCARED-P from CBCL GI symptoms.

## Load pacakages/Set themes
```{r}
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(arm)
library(gridExtra)
source('helperFunctions.R')

# Plot theme
mytheme = theme_bw() 
theme_set(mytheme)
```

# Load data 

## Load in HBN Complete Case Training Set
```{r}
hbnCompleteTrain = read.csv('../cleanData/hbnTrainComplete.csv', stringsAsFactors = FALSE)

# Complete-cases analysis: filter out where SCARED-P is NA
hbnCompleteTrainScaredParent = filter(hbnCompleteTrain, !is.na(scaredSumParent))

# Recode sex
hbnCompleteTrainScaredParent = mutate(hbnCompleteTrainScaredParent, 
                                      sexOrig = ifelse(sex == 1, 'Female', 'Male'),
                                      sexContrast = ifelse(sexOrig == 'Male', -.5, .5))

# get mean age
hbnFull = read.csv(file = '../cleanData/fullHBN.csv', stringsAsFactors = FALSE)
meanAge = mean(hbnFull$age)
```


## Load in SB/ELFK Scared
```{r}
## Load in SB & ELFK Data
sb = read.csv('../cleanData/sbDataClean.csv', stringsAsFactors = F) %>% mutate(., study = 'sb')
elfk = read.csv('../cleanData/elfkDataClean.csv', stringsAsFactors = F) %>% mutate(., study = 'elfk')

# Recode sex and name variables the same way as in HBN
sb = mutate(sb, sexOrig = ifelse(Sex == 1, 'Female', 'Male'),
            sexContrast = ifelse(sexOrig == 'Male', -.5, .5)) %>%
  rename(age = bl_age_gi_new, cbclGISum = CBCL_GI_sum, scaredSumParent = sum_scared) %>%
  mutate(ageCenter = age - meanAge)

elfk = mutate(elfk, sexOrig = ifelse(Sex == 1, 'Female', 'Male'),
            sexContrast = ifelse(sexOrig == 'Male', -.5, .5)) %>%
  rename(age = bl_age_gi_new, cbclGISum = CBCL_GI_sum, scaredSumParent = sum_scared) %>%
  mutate(ageCenter = age - meanAge)
```


# Linear Regresson on HBN Training Data
```{r, results='hide'}
hbnScaredPLinearReg = stan_glm(data = hbnCompleteTrainScaredParent, scaredSumParent ~ cbclGISum*sexContrast + ageCenter)
```

HBN Model Summary
```{r}
summary(hbnScaredPLinearReg)
```
# Define a data frame of predictor values for which to plot model predictions

We'll use the same dataframe to get predictions for all cohorts

  * GI symptoms - ranging from 1-8
  * sexContrast = 0 --- represents the 'average' sex 
  * ageCenter = 0 -- predictions for the mean age in the HBN cohort (`r meanAge`)
```{r}
predMatrix = expand.grid(cbclGISum = 0:8, sexContrast = c(0), ageCenter = c(0)) %>%
  mutate(., ageBin= as.factor(ageCenter + meanAge))
```

## Pull HBN Model Predictions

```{r}
# Get predictions by extracting posterior draws of the linear predictor (posterior_linpred()), then get summary statistics from the posterior: median, and .025 and .975 quantiles, then put into dataframe
scaredParentHBNPreds = posterior_linpred(hbnScaredPLinearReg, newdata = predMatrix)
scaredParentHBNPreds = t(cbind(apply(scaredParentHBNPreds,2, quantile, c(.025, .5, .975)))) 
scaredParentHBNPreds = data.frame(scaredParentHBNPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'HBN')
```
## Fit the same linear regression to SB Data
```{r, results='hide'}
sbScaredLinearReg = stan_glm(data = sb, scaredSumParent ~ cbclGISum*sexContrast + ageCenter)
```

SB Model Summary
```{r}
summary(sbScaredLinearReg)
```

## Pull SB Model Predictions
```{r}
scaredParentSbLinearPreds = posterior_linpred(sbScaredLinearReg, newdata = predMatrix)
scaredParentSbLinearPreds = t(cbind(apply(scaredParentSbLinearPreds,2, quantile, c(.025, .5, .975)))) 
scaredParentSbLinearPreds = data.frame(scaredParentSbLinearPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'LA')
```

## Fit the same linear regression to ELFK Data
```{r, results='hide'}
elfkScaredLinearReg = stan_glm(data = elfk, scaredSumParent ~ cbclGISum*sexContrast + ageCenter)
```

ELFK Model Summary
```{r}
summary(elfkScaredLinearReg)
```

## Pull ELFK Model Predictions
```{r}
elfkModelElfkPreds = posterior_linpred(elfkScaredLinearReg, newdata = predMatrix)
elfkModelElfkPreds = t(cbind(apply(elfkModelElfkPreds,2, quantile, c(.025, .5, .975)))) 
elfkModelElfkPreds = data.frame(elfkModelElfkPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'NYC')
```

## Plot models from every dataset together!
```{r}
# bind predictions from all three models together
all3Models = rbind(elfkModelElfkPreds, scaredParentSbLinearPreds, scaredParentHBNPreds)

# Remove predictions for the LA/NYC cohorts for GI scores > 4 (no participants actually have scores above 4 in these datasets)
all3Models = filter(all3Models, !(model == 'NYC' & cbclGISum > 4),
                    !(model == 'LA' & cbclGISum > 4))

# Plot predictions for each model for each cohort
replicationPlot = ggplot(data = filter(all3Models, ageCenter == 0)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 25, lty = 2, lwd = 1) + 
  geom_line(aes(x = cbclGISum, y = X50., group = model, color = model), lwd = 2) +
  geom_ribbon(aes(x = cbclGISum, y = X50., ymin = X2.5., ymax = X97.5., group = model, fill = model), alpha= .3) +
  scale_fill_brewer(palette = 'Set1') +
  scale_color_brewer(palette = 'Set1') +
  labs(x = "Sum of CBCL GI Symptoms", y = 'Parent Report Total SCARED Score', title = 'A') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.title = element_blank()) 

replicationPlot
```

## Compare model posterior draws
```{r}
# pull posterior draws from each model
hbnDraws = as.data.frame(hbnScaredPLinearReg)
sbDraws = as.data.frame(sbScaredLinearReg)
elfkDraws = as.data.frame(elfkScaredLinearReg)

# label each dataset
hbnDraws$dataset = 'HBN'
sbDraws$dataset = 'LA'
elfkDraws$dataset = 'NYC'

# combine draws for models from each dataset
allDraws = rbind(hbnDraws, sbDraws, elfkDraws)

# Summarize posterior distributions for the GI sum predictor
allDrawsSummary = allDraws %>%
  group_by(dataset) %>%
  summarise(estimate = median(cbclGISum),
            lwr95 = quantile(cbclGISum, .025),
            upr95 = quantile(cbclGISum, .975),
            lwr80 = quantile(cbclGISum, .1),
            upr80 = quantile(cbclGISum, .9))

# plot posterior distribution summaries
replicationParamsPlot = ggplot(allDraws, aes(x = dataset, y = cbclGISum)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_errorbar(data = allDrawsSummary, aes(y = estimate, ymin = lwr95, ymax = upr95), width = .05, lwd = .5) +
  geom_errorbar(data = allDrawsSummary, aes(y = estimate, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = allDrawsSummary, aes(y = estimate)) +
  geom_flat_violin(aes(fill = dataset), position = position_nudge(x = .1, y = 0)) +
  scale_fill_brewer(palette = 'Set1') +
  scale_color_brewer(palette = 'Set1') +
  labs(x = "Cohort", y = 'Beta Estimate for GI Predictor', title = 'B') +
  theme(text = element_text(face = 'bold'), 
        legend.position = 'none') +
  scale_x_discrete(limits = c('NYC', 'LA', 'HBN')) +
  coord_flip()


replicationParamsPlot
```

## Arrange plot of predictions + params together
```{r}
pdf('../plots/replicationCohortsPlot.pdf', width = 8, height = 4)
grid.arrange(replicationPlot, replicationParamsPlot, ncol = 2, widths = c(1.5, 1))
dev.off()
```

## Save models out
```{r}
save(sbScaredLinearReg, elfkScaredLinearReg, hbnScaredPLinearReg, file = '../output/linearModelsReplication.rda')
```

# Repeat process with logistic regressions

## Run Logistic Regressions and Get Predictions
```{r, results='hide'}
# models for each dataset
hbnScaredPLogisticReg = stan_glm(data = hbnCompleteTrainScaredParent, scaredBinParent ~ cbclGISum*sexContrast + ageCenter, family= binomial(link = 'logit'), cores = 4)
sbScaredPLogisticReg = stan_glm(data = sb, scaredBin ~ cbclGISum*sexContrast + ageCenter, family= binomial(link = 'logit'), cores = 4)
elfkScaredPLogisticReg = stan_glm(data = elfk, scaredBin ~ cbclGISum*sexContrast + ageCenter, family= binomial(link = 'logit'), cores = 4)

# Model predictions for each dataset -- this time we use the invlogit() function to represent predictions as probabilities
sbModelLogitPreds  = invlogit(posterior_linpred(sbScaredPLogisticReg, newdata = predMatrix))
sbModelLogitPreds  = t(cbind(apply(sbModelLogitPreds ,2, quantile, c(.025, .5, .975)))) 
sbModelLogitPreds  = data.frame(sbModelLogitPreds ) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'LA')

elfkModelLogitPreds  = invlogit(posterior_linpred(elfkScaredPLogisticReg, newdata = predMatrix))
elfkModelLogitPreds  = t(cbind(apply(elfkModelLogitPreds ,2, quantile, c(.025, .5, .975)))) 
elfkModelLogitPreds  = data.frame(elfkModelLogitPreds ) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'NYC')

hbnModelLogitPreds  = invlogit(posterior_linpred(hbnScaredPLogisticReg, newdata = predMatrix))
hbnModelLogitPreds  = t(cbind(apply(hbnModelLogitPreds ,2, quantile, c(.025, .5, .975)))) 
hbnModelLogitPreds  = data.frame(hbnModelLogitPreds ) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'HBN')
```

## Bind predictions from all datasets together, filter out predictions where there is no data for SB/ELFK
```{r}
allLogitPreds = rbind(sbModelLogitPreds, elfkModelLogitPreds, hbnModelLogitPreds) %>%
  dplyr::filter(., !(cbclGISum > 4 & model != 'HBN'))

# plot
replicationPlotLogistic = ggplot(data = allLogitPreds) +
  geom_line(aes(x = cbclGISum, y = X50., group = model, color = model), lwd = 2) +
  geom_ribbon(aes(x = cbclGISum, y = X50., ymin = X2.5., ymax = X97.5., group = model, fill = model), alpha= .3) +
  scale_fill_brewer(palette = 'Set1') +
  scale_color_brewer(palette = 'Set1') +
  labs(x = "Sum of CBCL GI Symptoms", y = 'P(Meet SCARED-P Clinical Cutoff)') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.title = element_blank()) 

replicationPlotLogistic
```

## Posterior distributions for GI predictor in logistic regressions
```{r}
# pull posterior draws from each model
hbnDrawsLogistic = as.data.frame(hbnScaredPLogisticReg)
sbDrawsLogistic = as.data.frame(sbScaredPLogisticReg)
elfkDrawsLogistic = as.data.frame(elfkScaredPLogisticReg)

# label each dataset
hbnDrawsLogistic$dataset = 'HBN'
sbDrawsLogistic$dataset = 'LA'
elfkDrawsLogistic$dataset = 'NYC'

# combine draws for models from each dataset
allDrawsLogistic = rbind(hbnDrawsLogistic, sbDrawsLogistic, elfkDrawsLogistic)

# Summarize posterior distributions for the GI sum predictor

allDrawsSummaryLogistic = allDrawsLogistic %>%
  group_by(dataset) %>%
  summarise(estimate = median(cbclGISum),
            lwr95 = quantile(cbclGISum, .025),
            upr95 = quantile(cbclGISum, .975),
            lwr80 = quantile(cbclGISum, .1),
            upr80 = quantile(cbclGISum, .9))

# plot posterior distribution summaries
replicationParamsLogisticPlot = ggplot(allDrawsLogistic, aes(x = dataset, y = cbclGISum)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_errorbar(data = allDrawsSummaryLogistic, aes(y = estimate, ymin = lwr95, ymax = upr95), width = .05, lwd = .5) +
  geom_errorbar(data = allDrawsSummaryLogistic, aes(y = estimate, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = allDrawsSummaryLogistic, aes(y = estimate)) +
  geom_flat_violin(aes(fill = dataset), position = position_nudge(x = .1, y = 0)) +
  scale_fill_brewer(palette = 'Set1') +
  scale_color_brewer(palette = 'Set1') +
  labs(x = "Cohort", y = 'Beta Estimate for GI Predictor') +
  theme(text = element_text(face = 'bold'), 
        legend.position = 'none') +
  scale_x_discrete(limits = c('NYC', 'LA', 'HBN')) +
  coord_flip()


replicationParamsLogisticPlot
```

## Arrange plot of predictions + params together for logistic
```{r}
pdf('../plots/replicationCohortsLogisticPlot.pdf', width = 8, height = 4)
grid.arrange(replicationPlotLogistic, replicationParamsLogisticPlot, ncol = 2, widths = c(1.5, 1))
dev.off()
```

## Save logit models out
```{r}
save(sbScaredPLogisticReg, elfkScaredPLogisticReg, hbnScaredPLogisticReg, file = '../output/logisticModelsReplication.rda')
```

# Session Info
```{r}
sessionInfo()
```



