---
title: "2b: Examining Robustness of GI-Anxiety Associations to Child Anxiety Informat"
author: "Paul A. Bloom"
date: "June 21, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown runs models in parallel predicting SCARED-P, SCARED-C, and KSADS from CBCL GI items in the HBN training data. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Load pacakages/Set themes
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(arm)
library(gridExtra)
source('helperFunctions.R')

# Plot theme
mytheme = theme_bw() 
theme_set(mytheme)
```

## Load in HBN Complete Case Training Set

```{r}
hbnCompleteTrain = read.csv('../cleanData/hbnTrainComplete.csv', stringsAsFactors = FALSE)

# Recode sex
hbnCompleteTrain= mutate(hbnCompleteTrain,
                                      sexOrig = ifelse(sex == 1, 'Female', 'Male'),
                                      sexContrast = ifelse(sexOrig == 'Male', -.5, .5))

# For modeling each respective outcome, filter out NAs
hbnCompleteTrainScaredParent= filter(hbnCompleteTrain, !is.na(scaredSumParent))
hbnCompleteTrainScaredChild= filter(hbnCompleteTrain, !is.na(scaredSumChild))
hbnCompleteTrainKsads = filter(hbnCompleteTrain, !is.na(ksadsBin))


# get mean age
hbnFull = read.csv(file = '../cleanData/fullHBN.csv', stringsAsFactors = FALSE)
meanAge = mean(hbnFull$age)
```

# Models for scared child and ksads
```{r,results='hide'}
hbnReplicationScaredChildModel = stan_glm(data = hbnCompleteTrainScaredChild, scaredSumChild ~ cbclGISum*sexContrast + ageCenter)
summary(hbnReplicationScaredChildModel)

hbnReplicationKsadsModel = stan_glm(data = hbnCompleteTrainKsads, ksadsBin ~ cbclGISum*sexContrast + ageCenter,
                                    family = binomial(link = 'logit'))
```

## Summarize models
```{r}
summary(hbnReplicationScaredChildModel)
summary(hbnReplicationKsadsModel)
```

# Define prediction data frame
```{r}
predMatrix = expand.grid(cbclGISum = 0:8, sexContrast = c(0), ageCenter = c(0)) %>%
  mutate(., ageBin= as.factor(ageCenter + meanAge))
```

## SCARED-C predictions and plot

```{r}
# Get predictions by extracting posterior draws of the linear predictor
scaredChildHBNPreds = posterior_linpred(hbnReplicationScaredChildModel, newdata = predMatrix)
scaredChildHBNPreds = t(cbind(apply(scaredChildHBNPreds,2, quantile, c(.025, .5, .975)))) 
scaredChildHBNPreds = data.frame(scaredChildHBNPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'HBN')

ChildScaredContHBN = hbnCompleteTrainScaredChild %>%
  ggplot(data = ., aes(x = cbclGISum,y = scaredSumChild)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 25, lty = 2, lwd = 1) + 
  geom_jitter(width = .1, height = 0, alpha = .2, size = 1) +
  geom_line(data = scaredChildHBNPreds, aes(x = cbclGISum,y = X50., color = model), lwd = 1, show.legend = FALSE) +
  geom_ribbon(data = scaredChildHBNPreds, aes(x = cbclGISum, y = X50.,ymin = X2.5., ymax = X97.5., fill = model), alpha= .3) +
  scale_fill_brewer(palette = 'Set2') +
  scale_color_brewer(palette = 'Set2') +
  labs(x = "", y = 'Child Report Total SCARED Score', title = 'Child Report') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.position = 'none') +
  ylim(0, 81)
  
ChildScaredContHBN
```

## KSADS Predictions and Plot
```{r}
hbnKsadsModelPreds = invlogit(posterior_linpred(hbnReplicationKsadsModel, newdata = predMatrix))
hbnKsadsModelPreds = t(cbind(apply(hbnKsadsModelPreds,2, quantile, c(.025, .5, .975)))) 
hbnKsadsModelPreds = data.frame(hbnKsadsModelPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'KSADS')

# A dataframe of KSADS raw data summaries  -- what proportion of participants at each level of GI score actually had anxiety diagnoses on KSADS
actual = hbnCompleteTrainKsads %>%
  group_by(cbclGISum) %>%
  summarise(., propCutoff = sum(ksadsBin)/n(), n = n()) 

ksadsPlot = hbnCompleteTrainKsads %>%
  ggplot(data = ., aes(x = cbclGISum,y = ksadsBin)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = .5, lty = 3) +
  geom_point(data = actual, aes(x = cbclGISum, y = propCutoff, size = n)) + 
  geom_line(data = hbnKsadsModelPreds, aes(x = cbclGISum,y = X50., color = model), lwd = 2, show.legend = FALSE) + 
  geom_ribbon(data = hbnKsadsModelPreds, aes(x = cbclGISum, y = X50.,ymin = X2.5., ymax = X97.5., fill = model), alpha= .3, show.legend = FALSE) +
  ylim(0,1) +
  labs(x = "", y = 'P(KSADS Diagnosis)', title = 'B\nClinician Consensus') +
  scale_fill_brewer(palette = 'Set2') +
  scale_color_brewer(palette = 'Set2') + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.title = element_blank()) 

ksadsPlot
```

## Scared Parent Predictions and Plot
```{r, echo = FALSE}
# load the model object already run in the previous script
load('../output/linearModelsReplication.rda')

scaredParentHBNPreds = posterior_linpred(hbnScaredPLinearReg, newdata = predMatrix)
scaredParentHBNPreds = t(cbind(apply(scaredParentHBNPreds,2, quantile, c(.025, .5, .975)))) 
scaredParentHBNPreds = data.frame(scaredParentHBNPreds) %>%
  cbind(predMatrix, .) %>%
  mutate(., model = 'HBN')

ParentScaredContHBN = hbnCompleteTrainScaredParent %>%
  ggplot(data = ., aes(x = cbclGISum,y = scaredSumParent)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 25, lty = 2, lwd = 1) + 
  geom_jitter(width = .1, height = 0, alpha = .2, size = 1) +
  geom_line(data = scaredParentHBNPreds, aes(x = cbclGISum,y = X50.,
                                             color = model), lwd = 1, show.legend = FALSE) +
  geom_ribbon(data = scaredParentHBNPreds, aes(x = cbclGISum, y = X50.,ymin = X2.5., 
                                               ymax = X97.5.,fill = model , alpha= .3)) +
  scale_fill_brewer(palette = 'Set2') +
  scale_color_brewer(palette = 'Set2') +
  labs(x = "", y = 'Parent Report Total SCARED Score', title = 'Parent Report') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.position = 'none') +
  ylim(0, 81)

ParentScaredContHBN
```

## Parent + Child on one plot
```{r}
# Bind together predictions from both SCARED-P and SCARED-C
scaredParentHBNPreds$reporter = 'SCARED-P'
scaredChildHBNPreds$reporter = 'SCARED-C'
scaredHBNAllPreds = rbind(scaredChildHBNPreds, scaredParentHBNPreds)


# Reformat raw data for this as well
hbnCompleteTrainLong = tidyr::gather(hbnCompleteTrain, key = 'reporter', value = 'score', 
                                     scaredSumParent, scaredSumChild) %>%
  mutate(., reporter = ifelse(reporter == 'scaredSumParent', 'SCARED-P', 'SCARED-C'))



childParentPlot = hbnCompleteTrainLong %>%
  ggplot(data = ., aes(x = cbclGISum,y = score)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = 25, lty = 2, lwd = 1) + 
  geom_jitter(width = .1, height = 0, alpha = .2, size = 1, aes(color = reporter)) +
  geom_line(data = scaredHBNAllPreds, aes(x = cbclGISum,y = X50.,
                                             color = reporter), lwd = 1) +
  geom_ribbon(data = scaredHBNAllPreds, aes(x = cbclGISum, y = X50.,ymin = X2.5., 
                                               ymax = X97.5.,fill = reporter), alpha = .3) +
  scale_fill_brewer(palette = 'Set2') +
  scale_color_brewer(palette = 'Set2') +
  labs(x = "", y = 'Total SCARED Score', title = 'A', subtitle = 'Parent & Child Report') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.title = element_blank()) +
  ylim(0, 81)

childParentPlot

```

## Alternative KSADS Plot

```{r}
ksadsPlotAlt = hbnCompleteTrainKsads %>%
  ggplot(data = ., aes(x = cbclGISum,y = ksadsBin)) +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = .5, lty = 2) +
  geom_point(data = actual, aes(x = cbclGISum, y = propCutoff, size = n)) + 
  geom_line(data = hbnKsadsModelPreds, aes(x = cbclGISum,y = X50.), lwd = 1, show.legend = FALSE, color = 'purple2', alpha = .65) + 
  geom_ribbon(data = hbnKsadsModelPreds, aes(x = cbclGISum, y = X50.,ymin = X2.5., ymax = X97.5.), alpha= .15, show.legend = FALSE, fill = 'purple2') +
  ylim(0,1) +
  labs(x = "", y = 'P(KSADS Diagnosis)', title = 'B', subtitle = 'Clinician Consensus') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text = element_text(face = 'bold'),
        legend.title = element_blank()) 

ksadsPlotAlt
```


# Arranged plot option 1
```{r}
pdf('../plots/replicationMultiOutcomesPlot.pdf', width = 7, height = 4)
grid.arrange(ParentScaredContHBN, ChildScaredContHBN, ksadsPlot, ncol = 3, widths = c(2,2,3), bottom = 'Sum of CBCL GI Symptoms')
dev.off()
```

# Arranged plot option 2
```{r}
pdf('../plots/replicationMultiOutcomesPlotOption2.pdf', width = 7, height = 4)
grid.arrange(childParentPlot, ksadsPlotAlt, ncol = 2, widths = c(4,3), bottom = 'Sum of CBCL GI Symptoms')
dev.off()
```


# Save robusness models out

```{r}
save(hbnReplicationKsadsModel, hbnReplicationScaredChildModel, hbnScaredPLinearReg, file = '../output/hbnModelsRobustness.rda')
```

# Sex models

Models here have sex as the sole predictor -- looking at associations between sex and the different anxiety outcomes irrespective of GI 
```{r,results='hide'}
scaredPgender = stan_glm(data = hbnCompleteTrainScaredParent, scaredSumParent ~ sex, cores = 4)
scaredCgender = stan_glm(data = hbnCompleteTrainScaredChild, scaredSumChild ~ sex, cores = 4)
ksadsgender = stan_glm(data = hbnCompleteTrainKsads, ksadsBin ~ sex, family = binomial(link = 'logit'), cores = 4)

# save models out
save(scaredPgender, scaredCgender, ksadsgender, file = '../output/genderModels.rda')
```

## Export predictions from KSADS model for the Shiny app beta
```{r}
# Grid of predictions for use in the shiny app
shinyGrid = expand.grid(sexContrast = c(-.5, .5), ageCenter = -6:10, cbclGISum = 0:8) %>%
  mutate(., ageBin = round(ageCenter + meanAge))

# Get predictions for shiny app
shinyPreds = invlogit(posterior_linpred(hbnReplicationKsadsModel, newdata = shinyGrid))
shinyPreds = t(cbind(apply(shinyPreds,2, quantile, c(.025, .1, .5, .9, .975)))) 
shinyPreds = data.frame(shinyPreds) %>%
  cbind(shinyGrid, .) %>%
  mutate(., sexOrig = ifelse(sexContrast == .5, 'Female', 'Male'))

# Save out shiny app predictions
save(shinyPreds, file = 'giShinyApp/data/shinyPreds.rda')
```


# Session Info
```{r}
sessionInfo()
```



