---
title: "3d: Compile HBN CV Results"
author: "Paul A. Bloom"
date: "June 21, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown compiles cross-validation results across pipelines, metrics, and outcomes from the HBN training set. It also runs CV using the RMSE metric that wasn't used in 3A-C. It outputs a plot comparing all distributions of cv performance.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

# Load pacakages/Set themes
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(arm)
library(cowplot)
source('helperFunctions.R')
source('cvFunction.R')

# Plot theme
mytheme = theme_bw() + theme(panel.grid.major = element_blank(), 
                             axis.text=element_text(size=14),
                             axis.title.x=element_text(size=14,face="bold"),
                             axis.title.y=element_text(size=14, face="bold"),
                             plot.title=element_text(size=20, hjust = 0.5))
theme_set(mytheme)

# Color palette
myPal = c('#2b8cbe', '#88419d', '#238b45','#cb181d')

# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

# Parent CV

## Load in HBN Training Sets

```{r}
# Complete
hbnCompleteTrain = read.csv('../cleanData/hbnTrainComplete.csv', stringsAsFactors = FALSE)
hbnCompleteTrainScaredParent = filter(hbnCompleteTrain, !is.na(scaredSumParent)) %>%
  mutate(missingData = 'complete')

# 3NN
hbn3NNTrain = read.csv('../cleanData/hbnTrain3NN.csv', stringsAsFactors = FALSE) %>%
  mutate(missingData = '3NN')

# 9NN
hbn9NNTrain = read.csv('../cleanData/hbnTrain9NN.csv', stringsAsFactors = FALSE) %>%
  mutate(missingData = '9NN')
```


## RMSE CV for Linear Regression - Define Linear Regresson Formulas

```{r}
sumFormulas = list(scaredSumParent ~ sex + ageCenter + cbclGISum, 
                   scaredSumParent ~ sex + ageCenter*cbclGISum,
                   scaredSumParent ~ sex*cbclGISum + ageCenter, 
                   scaredSumParent ~ cbclGISum*ageCenter*sex)

indivFormulas = list(scaredSumParent ~ sex + ageCenter + nausea + stomachache_cramps + vomiting + constipated,
                     scaredSumParent ~ sex + nausea*ageCenter + stomachache_cramps*ageCenter + vomiting*ageCenter + constipated*ageCenter,
                     scaredSumParent ~ ageCenter + nausea*sex + stomachache_cramps*sex + vomiting*sex + constipated*sex,
                     scaredSumParent ~ nausea*sex*ageCenter + stomachache_cramps*sex*ageCenter + vomiting*sex*ageCenter + constipated*sex*ageCenter)


noGiFormulas = list(scaredSumParent ~ ageCenter,
                    scaredSumParent ~ sex,
                    scaredSumParent ~ ageCenter + sex,
                    scaredSumParent ~ ageCenter*sex)

interceptFormula = list(scaredSumParent ~ 1)
```

## Define logistic regression formulas

```{r}
sumFormulasScaredBinParent = list(scaredBinParent ~ sex + ageCenter + cbclGISum, 
                   scaredBinParent ~ sex + ageCenter*cbclGISum,
                   scaredBinParent ~ sex*cbclGISum + ageCenter, 
                   scaredBinParent ~ cbclGISum*ageCenter*sex)

indivFormulasScaredBinParent = list(scaredBinParent ~ sex + ageCenter + nausea + stomachache_cramps + vomiting + constipated,
                     scaredBinParent ~ sex + nausea*ageCenter + stomachache_cramps*ageCenter + vomiting*ageCenter + constipated*ageCenter,
                     scaredBinParent ~ ageCenter + nausea*sex + stomachache_cramps*sex + vomiting*sex + constipated*sex,
                     scaredBinParent ~ nausea*sex*ageCenter + stomachache_cramps*sex*ageCenter + vomiting*sex*ageCenter + constipated*sex*ageCenter)


noGiFormulasScaredBinParent = list(scaredBinParent ~ ageCenter,
                    scaredBinParent ~ sex,
                    scaredBinParent ~ ageCenter + sex,
                    scaredBinParent ~ ageCenter*sex)

interceptFormulaScaredBinParent = list(scaredBinParent ~ 1)
```

## RMSE: Run cross-val on each training set

```{r}
# number of rounds to run
numRounds = 100

# multiple training sets (complete cases, 3NN imputation, 9NN imputation)
trainSets = list(hbnCompleteTrainScaredParent, hbn3NNTrain, hbn9NNTrain)

# data frame to store results of cross-val with each training set
cvScaredRMSEParentOutputs = data.frame(index = 1:length(trainSets), trainSet = c('complete', '3NN', '9NN'))

for (ii in 1:length(trainSets)){
  print(ii)
  # select the training set
  trainSet = trainSets[[ii]]
  
  # Run the crossval & save to dataframe -- using the cvManyLinearModels() custom function
  # Linear regression cv with RMSE as the metric
  cvLinear = cvManyLinearModels(inputData = trainSet, outcomeColumn = 'scaredSumParent', 
                                metric = rMSE, numFolds = 10, cvRounds = numRounds, modType = lm,
                                sumFormulas = sumFormulas, indivFormulas = indivFormulas, 
                                noGiFormulas = noGiFormulas, interceptFormula = interceptFormula)
  

  # Order factor levels of model forumulations for plotting
  cvLinear[[2]]$ModelSetOrdered = ordered(cvLinear[[2]]$ModelSet, c('GI Sum Score', 'GI Indiv. Items', 'No GI Term', 'Intercept Only'))

  # Order factor levels of model specification within model formulation for plotting
  cvLinear[[2]]$model = ordered(cvLinear[[2]]$model, c('No Interactions', 'Age*GI', 'Sex*GI', 'Age*Sex*GI', 'Age', 'Sex', 'Age + Sex', 'Age*Sex', 'Intercept Only'))

  # Add cv objects to output df
  cvScaredRMSEParentOutputs$cvLinear[ii] = list(cvLinear)

  # Make plot comparing cross-val distributions
  hbnLinearRegScaredParentCV = ggplot(cvLinear[[2]], aes(x = model, y = median)) +
    geom_errorbar(aes(ymin = upr80, ymax = lwr80, color = ModelSet), width = 0, lwd = 1) +
    geom_errorbar(aes(ymin = upr95, ymax = lwr95, color = ModelSet), width = .1) +
    geom_point(size = 2) +
    facet_grid(~ModelSetOrdered, scales = 'free_x') +
    theme(axis.text.x = element_text(angle =90, hjust = 1),
          legend.position = 'none',
          plot.title = element_text(hjust = 0, size = 15)) +
    labs(x = '', y = 'RMSE', title = 'A') +
    scale_color_manual(values = myPal)
  

  # Store infor on which model is best, as well as direct comparisons
  bestLinearModelIndivResults = dplyr::select(cvLinear[[1]], 
                    sum = contains(paste0('Sum', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'GI Sum Score']))),
                    indiv = contains(paste0('Indiv', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'GI Indiv. Items']))),
                    noGi = contains(paste0('NoGI', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'No GI Term']))),
                    intercept = contains('Int'))

  # Get percentages of folds for which models were better than other models usinc percentBetter() function
  sumOverNoGiLinear =  percentBetter(bestLinearModelIndivResults$noGi, bestLinearModelIndivResults$sum)
  sumOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$sum)
  indivOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$indiv)
  indivOverNoGiLinear = percentBetter(bestLinearModelIndivResults$noGi, bestLinearModelIndivResults$indiv)
  indivOverSumLinear = percentBetter(bestLinearModelIndivResults$sum, bestLinearModelIndivResults$indiv)
  noGiOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$noGi)
  
  # Put model comparisons in output df
  cvScaredRMSEParentOutputs$modelComparisonsLinear[ii] = list(list('sumOverNoGi' = sumOverNoGiLinear, 
                                                                   'sumOverInt' = sumOverIntLinear,
                                                               'indivOverInt' = indivOverIntLinear, 
                                                               'indivOverNoGi' = indivOverNoGiLinear,
                                                               'indivOverSum' = indivOverSumLinear, 
                                                               'noGiOverInt' = noGiOverIntLinear))
  
  # Make 'within-subjects' scatter plots
  # GI Sum vs. No-GI
  pSumNoGiLinear = ggplot(bestLinearModelIndivResults, aes(x = sum, y = noGi)) +
  geom_point(alpha = .3) +
  geom_abline(slope = 1, intercept = 0) +
  ylim(6, 15) + xlim(6, 15) +
  theme_classic() +
  labs(x= 'GI Sum', y = 'No-GI', title = 'B') +
  annotate("text", x = 11, y = 8, label = paste0('GI model better\n ', 100*sumOverNoGiLinear, '% of folds'),
           size = 2)
  
  # GI Indiv. Items vs. No-GI
  pIndivNoGiLinear = ggplot(bestLinearModelIndivResults, aes(x = indiv, y = noGi)) +
    geom_point(alpha = .3) +
    geom_abline(slope = 1, intercept = 0) +
    ylim(6, 15) + xlim(6, 15) +
    theme_classic() +
    labs(x= 'GI Indiv Items', y = 'No-GI', title = 'C') +
    annotate("text", x = 11, y = 8, label = paste0('GI model better\n ', 100*indivOverNoGiLinear, '% of folds'),
             size = 2)
  
  # GI Sum vs. No-GI
  pSumIndivLinear = ggplot(bestLinearModelIndivResults, aes(y = sum, x = indiv)) +
    geom_point(alpha = .3) +
    geom_abline(slope = 1, intercept = 0) +
    ylim(6, 15) + xlim(6, 15) +
    theme_classic() +
    labs(y= 'GI Sum', x = 'GI Indiv Items', title = 'D') +
    annotate("text", x = 11, y = 8, label = paste0('Indiv. Items Better\n ', 100*indivOverSumLinear, '% of folds'),
             size = 2)

  
  # Put all plots together and save pdf
  pdf(paste0('../plots/hbnLinearRegScaredParentCV_', trainSet$missingData[1], '_RMSE.pdf'), height = 6, width = 8)
  gridExtra::grid.arrange(hbnLinearRegScaredParentCV, pSumNoGiLinear, pIndivNoGiLinear, pSumIndivLinear, 
                          layout_matrix = rbind(c(1,1,1),c(2,3,4)))
  dev.off()
}
```

```{r}
# Save cross-val outputs
save(cvScaredRMSEParentOutputs, file = '../output/cvScaredParentOutputsRMSE.rda', compress = TRUE)
```


# Child RMSE CV


## Load in training sets

```{r}
hbnCompleteTrain = read.csv('../cleanData/hbnTrainComplete.csv', stringsAsFactors = FALSE)
hbn3NNTrain = read.csv('../cleanData/hbnTrain3NN.csv', stringsAsFactors = FALSE) %>%
  mutate(missingData = '3NN')
hbn9NNTrain = read.csv('../cleanData/hbnTrain9NN.csv', stringsAsFactors = FALSE) %>%
  mutate(missingData = '9NN')
hbnCompleteTrainScaredChild = filter(hbnCompleteTrain, !is.na(scaredSumChild)) %>%
  mutate(missingData = 'complete')
```


## Define linear regression formulas for child CV

```{r}
sumFormulas = list(scaredSumChild ~ sex + ageCenter + cbclGISum, 
                   scaredSumChild ~ sex + ageCenter*cbclGISum,
                   scaredSumChild ~ sex*cbclGISum + ageCenter, 
                   scaredSumChild ~ cbclGISum*ageCenter*sex)

indivFormulas = list(scaredSumChild ~ sex + ageCenter + nausea + stomachache_cramps + vomiting + constipated,
                     scaredSumChild ~ sex + nausea*ageCenter + stomachache_cramps*ageCenter + vomiting*ageCenter + constipated*ageCenter,
                     scaredSumChild ~ ageCenter + nausea*sex + stomachache_cramps*sex + vomiting*sex + constipated*sex,
                     scaredSumChild ~ nausea*sex*ageCenter + stomachache_cramps*sex*ageCenter + vomiting*sex*ageCenter + constipated*sex*ageCenter)


noGiFormulas = list(scaredSumChild ~ ageCenter,
                    scaredSumChild ~ sex,
                    scaredSumChild ~ ageCenter + sex,
                    scaredSumChild ~ ageCenter*sex)

interceptFormula = list(scaredSumChild ~ 1)

```

## Logistic regression formula definitions

```{r}
sumFormulasScaredBinChild = list(scaredBinChild ~ sex + ageCenter + cbclGISum, 
                   scaredBinChild ~ sex + ageCenter*cbclGISum,
                   scaredBinChild ~ sex*cbclGISum + ageCenter, 
                   scaredBinChild ~ cbclGISum*ageCenter*sex)

indivFormulasScaredBinChild = list(scaredBinChild ~ sex + ageCenter + nausea + stomachache_cramps + vomiting + constipated,
                     scaredBinChild ~ sex + nausea*ageCenter + stomachache_cramps*ageCenter + vomiting*ageCenter + constipated*ageCenter,
                     scaredBinChild ~ ageCenter + nausea*sex + stomachache_cramps*sex + vomiting*sex + constipated*sex,
                     scaredBinChild ~ nausea*sex*ageCenter + stomachache_cramps*sex*ageCenter + vomiting*sex*ageCenter + constipated*sex*ageCenter)


noGiFormulasScaredBinChild = list(scaredBinChild ~ ageCenter,
                    scaredBinChild ~ sex,
                    scaredBinChild ~ ageCenter + sex,
                    scaredBinChild ~ ageCenter*sex)

interceptFormulaScaredBinChild = list(scaredBinChild ~ 1)
```

## Run RMSE child cross-val on each training set

```{r}
# multiple training sets (complete cases, 3NN imputation, 9NN imputation)
trainSets = list(hbnCompleteTrainScaredChild, hbn3NNTrain, hbn9NNTrain)

# data frame to store results of cross-val with each training set
cvScaredRMSEChildOutputs = data.frame(index = 1:length(trainSets), trainSet = c('complete', '3NN', '9NN'))

for (ii in 1:length(trainSets)){
  print(ii)
  # select the training set
  trainSet = trainSets[[ii]]
  
  # Run the crossval & save to dataframe
  cvLinear = cvManyLinearModels(inputData = trainSet, outcomeColumn = 'scaredSumChild', 
                                metric = rMSE, numFolds = 10, cvRounds = numRounds, modType = lm,
                                sumFormulas = sumFormulas, indivFormulas = indivFormulas, 
                                noGiFormulas = noGiFormulas, interceptFormula = interceptFormula)
  

  # Order factor levels of model forumulations for plotting
  cvLinear[[2]]$ModelSetOrdered = ordered(cvLinear[[2]]$ModelSet, c('GI Sum Score', 'GI Indiv. Items', 'No GI Term', 'Intercept Only'))

  # Order factor levels of model specification within model formulation for plotting
  cvLinear[[2]]$model = ordered(cvLinear[[2]]$model, c('No Interactions', 'Age*GI', 'Sex*GI', 'Age*Sex*GI', 'Age', 'Sex', 'Age + Sex', 'Age*Sex', 'Intercept Only'))

  cvScaredRMSEChildOutputs$cvLinear[ii] = list(cvLinear)

  # Make plot comparing cross-val distributions
  hbnLinearRegScaredChildCV = ggplot(cvLinear[[2]], aes(x = model, y = median)) +
    geom_errorbar(aes(ymin = upr80, ymax = lwr80, color = ModelSet), width = 0, lwd = 1) +
    geom_errorbar(aes(ymin = upr95, ymax = lwr95, color = ModelSet), width = .1) +
    geom_point(size = 2) +
    facet_grid(~ModelSetOrdered, scales = 'free_x') +
    theme(axis.text.x = element_text(angle =90, hjust = 1),
          legend.position = 'none',
          plot.title = element_text(hjust = 0, size = 15)) +
    labs(x = '', y = 'RMSE', title = 'A') +
    scale_color_manual(values = myPal)
  

  # Store infor on which model is best, as well as direct comparisons
  bestLinearModelIndivResults = dplyr::select(cvLinear[[1]], 
                    sum = contains(paste0('Sum', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'GI Sum Score']))),
                    indiv = contains(paste0('Indiv', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'GI Indiv. Items']))),
                    noGi = contains(paste0('NoGI', as.character(cvLinear[[3]]$modelNum[cvLinear[[3]]$ModelSet == 'No GI Term']))),
                    intercept = contains('Int'))

  sumOverNoGiLinear =  percentBetter(bestLinearModelIndivResults$noGi, bestLinearModelIndivResults$sum)
  sumOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$sum)
  indivOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$indiv)
  indivOverNoGiLinear = percentBetter(bestLinearModelIndivResults$noGi, bestLinearModelIndivResults$indiv)
  indivOverSumLinear = percentBetter(bestLinearModelIndivResults$sum, bestLinearModelIndivResults$indiv)
  noGiOverIntLinear = percentBetter(bestLinearModelIndivResults$intercept, bestLinearModelIndivResults$noGi)
  
  cvScaredRMSEChildOutputs$modelComparisonsLinear[ii] = list(list('sumOverNoGi' = sumOverNoGiLinear, 'sumOverInt' = sumOverIntLinear,
                                                               'indivOverInt' = indivOverIntLinear, 'indivOverNoGi' = indivOverNoGiLinear,
                                                               'indivOverSum' = indivOverSumLinear, 'noGiOverInt' = noGiOverIntLinear))
  
  # Make 'within-subjects' scatter plots
  pSumNoGiLinear = ggplot(bestLinearModelIndivResults, aes(x = sum, y = noGi)) +
  geom_point(alpha = .3) +
  geom_abline(slope = 1, intercept = 0) +
  ylim(8, 17) + xlim(8, 17) +
  theme_classic() +
  labs(x= 'GI Sum', y = 'No-GI', title = 'B') +
  annotate("text", x = 13, y = 9, label = paste0('GI model better\n ', 100*sumOverNoGiLinear, '% of folds'),
           size = 2)
  
  pIndivNoGiLinear = ggplot(bestLinearModelIndivResults, aes(x = indiv, y = noGi)) +
    geom_point(alpha = .3) +
    geom_abline(slope = 1, intercept = 0) +
    ylim(8, 17) + xlim(8, 17) +
    theme_classic() +
    labs(x= 'GI Indiv Items', y = 'No-GI', title = 'C') +
    annotate("text", x = 13, y = 9, label = paste0('GI model better\n ', 100*indivOverNoGiLinear, '% of folds'),
             size = 2)
  
  pSumIndivLinear = ggplot(bestLinearModelIndivResults, aes(y = sum, x = indiv)) +
    geom_point(alpha = .3) +
    geom_abline(slope = 1, intercept = 0) +
    ylim(8, 17) + xlim(8, 17) +
    theme_classic() +
    labs(y= 'GI Sum', x = 'GI Indiv Items', title = 'D') +
    annotate("text", x = 13, y = 9, label = paste0('Indiv. Items Better\n ', 100*indivOverSumLinear, '% of folds'),
             size = 2)

  
  # Put all plots together and save pdf
  pdf(paste0('../plots/hbnLinearRegScaredChildCV_', trainSet$missingData[1], '_RMSE.pdf'), height = 6, width = 8)
  gridExtra::grid.arrange(hbnLinearRegScaredChildCV, pSumNoGiLinear, pIndivNoGiLinear, pSumIndivLinear, 
                          layout_matrix = rbind(c(1,1,1),c(2,3,4)))
  dev.off()
}
```

```{r}
# Save cross-val outputs
save(cvScaredRMSEChildOutputs, file = '../output/cvScaredChildOutputsRMSE.rda', compress = TRUE)
```


# Plots comparing CV RMSE & Q2 across pipelines for both SCARED-C and SCARED-P

Load Q2 CV summaries
```{r}
load('../output/cvScaredParentOutputs.rda')
load('../output/cvScaredChildOutputs.rda')
load('../output/cvKsadsOutputs.rda')
```

## Combine CV info for parent/child SCARED across all pipelines
```{r}
# label each dataframe with reporter and pipeline

# RMSE
childCompleteBestRMSE = cvScaredRMSEChildOutputs$cvLinear[[1]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = 'Complete Cases')
child3NNBestRMSE = cvScaredRMSEChildOutputs$cvLinear[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '3NN Imputation')
child9NNBestRMSE = cvScaredRMSEChildOutputs$cvLinear[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '9NN Imputation')

parentCompleteBestRMSE = cvScaredRMSEParentOutputs$cvLinear[[1]]$`Selected Models`  %>%
  mutate(Reporter = 'Parent Report', Pipeline = 'Complete Cases')
parent3NNBestRMSE = cvScaredRMSEParentOutputs$cvLinear[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '3NN Imputation')
parent9NNBestRMSE = cvScaredRMSEParentOutputs$cvLinear[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '9NN Imputation')

# Q2
childCompleteBestQ2 = cvScaredChildOutputs$cvLinear[[1]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = 'Complete Cases')
child3NNBestQ2 = cvScaredChildOutputs$cvLinear[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '3NN Imputation')
child9NNBestQ2 = cvScaredChildOutputs$cvLinear[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '9NN Imputation')

parentCompleteBestQ2 = cvScaredParentOutputs$cvLinear[[1]]$`Selected Models`  %>%
  mutate(Reporter = 'Parent Report', Pipeline = 'Complete Cases')
parent3NNBestQ2 = cvScaredParentOutputs$cvLinear[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '3NN Imputation')
parent9NNBestQ2 = cvScaredParentOutputs$cvLinear[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '9NN Imputation')

```

## Pull all CV results into one summary dataframe (for each outcome)

Reorder factor levels here for plotting too
```{r}
allRMSESummary = rbind(childCompleteBestRMSE, child3NNBestRMSE, child9NNBestRMSE, 
                       parentCompleteBestRMSE, parent3NNBestRMSE, parent9NNBestRMSE) %>%
  mutate(Reporter = factor(Reporter, levels = c('Parent Report', 'Child Report')))


allQ2Summary = rbind(childCompleteBestQ2, child3NNBestQ2, child9NNBestQ2, 
                     parentCompleteBestQ2, parent3NNBestQ2, parent9NNBestQ2) %>%
  mutate(Reporter = factor(Reporter, levels = c('Parent Report', 'Child Report')))
```

## Plots for RMSE and Q2 CV
```{r}
allRMSEPlot = ggplot(allRMSESummary, aes(x = ModelSet, y = median, color = Pipeline)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  facet_grid(~Reporter) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15)) +
  labs(y = 'RMSE', x = '', title = 'A', subtitle = 'Continuous Anxiety Symptoms')

allQ2Plot = ggplot(allQ2Summary, aes(x = ModelSet, y = median, color = Pipeline)) +
  geom_hline(yintercept = 0, lty = 2) + 
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  facet_grid(~Reporter) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15),
        legend.position = 'none') +
  labs(y = bquote(~q^2), x = '', title = 'B', subtitle = 'Continuous Anxiety Symptoms') 


```

## Combine CV info for ksads across pipelines

Log loss CV here
```{r}

# ksads
ksadsCompleteBest = cvKsadsOutputs$cvLogistic[[1]]$`Selected Models` %>%
  mutate(Pipeline = 'Complete Cases', Reporter = 'Clinician Consensus')
ksads3NNBest= cvKsadsOutputs$cvLogistic[[2]]$`Selected Models` %>%
  mutate(Pipeline = '3NN Imputation', Reporter = 'Clinician Consensus')
ksads9NNBest = cvKsadsOutputs$cvLogistic[[3]]$`Selected Models` %>%
  mutate(Pipeline = '9NN Imputation', Reporter = 'Clinician Consensus')

# SCARED-C
childCompleteBestLogLoss = cvScaredChildOutputs$cvLogistic[[1]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = 'Complete Cases')
child3NNBestLogLoss = cvScaredChildOutputs$cvLogistic[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '3NN Imputation')
child9NNBestLogLoss = cvScaredChildOutputs$cvLogistic[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Child Report', Pipeline = '9NN Imputation')

# SCARED-P
parentCompleteBestLogLoss = cvScaredParentOutputs$cvLogistic[[1]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = 'Complete Cases')
parent3NNBestLogLoss = cvScaredParentOutputs$cvLogistic[[2]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '3NN Imputation')
parent9NNBestLogLoss = cvScaredParentOutputs$cvLogistic[[3]]$`Selected Models` %>%
  mutate(Reporter = 'Parent Report', Pipeline = '9NN Imputation')

# Summary of all log loss CV
allLogLossSummary = rbind(ksadsCompleteBest, ksads3NNBest, ksads9NNBest, 
                          childCompleteBestLogLoss, child3NNBestLogLoss, child9NNBestLogLoss,
                          parentCompleteBestLogLoss, parent3NNBestLogLoss, parent9NNBestLogLoss)

# Reorder reporter factor levels
allLogLossSummary$Reporter = ordered(allLogLossSummary$Reporter, c('Parent Report', 'Child Report', 'Clinician Consensus'))


# Plot!
allLogLossPlot = ggplot(allLogLossSummary, aes(x = ModelSet, y = median, color = Pipeline)) +
  facet_grid(~Reporter) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15),
        legend.position = 'none') +
  labs(y = 'Log Loss', x = '', title = 'C', subtitle = 'Binary Clinical Cutoff/Diagnoses')

```

# Combine plots for multipanel CV summary plot

Using cowplot::plot_grid()

```{r}
cvComparison = plot_grid(allRMSEPlot, allQ2Plot, allLogLossPlot, ncol = 1, align = 'v', axis = 'l')
save_plot(filename = '../plots/suppCvComparison.pdf', cvComparison, base_height = 9, base_width = 8)
```

# Session Info
```{r}
sessionInfo()
```
