---
title: "4a: Validation of GI-anxiety models in HBN holdout data  -- complete cases pipeline"
author: "Paul A. Bloom"
date: "September 10, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown calculates validation performance metrics for GI-anxiety models trained on the HBN training data on the HBN holdout data using permutation and bootstrapping. Outputs are plots and model validation stats. This markdown uses models fit to the complete-cases pipeline. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Load pacakages/Set themes
```{r}
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(pROC)
library(gridExtra)

# Plot theme
mytheme = theme_bw() 
theme_set(mytheme)

# source helper functions
source('helperFunctions.R')

# color palette
myPal3 = c('#2b8cbe', '#88419d','#cb181d')
myPal3_reorder = c('#88419d', '#2b8cbe','#cb181d')
myPal4 = c('#2b8cbe', '#88419d', '#238b45','#cb181d')
myPal4_reorder = c('#88419d', '#2b8cbe', '#238b45','#cb181d')

# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```
# Number of iterations (will affect runtime)

```{r}
nPerms = 10000
nBoots = 10000
```

## Load in HBN Test Set

```{r}
hbnTest = read.csv('../cleanData/hbnTestComplete.csv', stringsAsFactors = FALSE)

## Make test set templates for predictions
hbnScaredChildTestTemplate = dplyr::select(hbnTest, -scaredSumParent, -scaredBinParent, -ksadsBin) %>%
  dplyr::filter(., complete.cases(.))
hbnScaredParentTestTemplate = dplyr::select(hbnTest, -scaredSumChild, -scaredBinChild, -ksadsBin) %>%
  dplyr::filter(., complete.cases(.))
hbnKsadsTest =dplyr::select(hbnTest, -scaredSumChild, -scaredBinChild, -scaredSumParent, -scaredBinParent) %>%
  dplyr::filter(., complete.cases(.))
```


# Load model objects
```{r}
load('../output/scaredParentModels.rda')
load('../output/scaredChildModels.rda')
load('../output/KsadsModels.rda')
```


# Get predictions 
```{r}
#Make predictions on the test set -- use templates so as not to overwrite previous prediction columns
hbnScaredChildTest = makePreds(testData = hbnScaredChildTestTemplate, modelsFrame = completeScaredChildLinearModFrame, modelType = 'linear')
hbnScaredParentTest = makePreds(testData = hbnScaredParentTestTemplate, modelsFrame = completeScaredParentLinearModFrame, modelType = 'linear')

hbnScaredChildBinTest = makePreds(testData = hbnScaredChildTestTemplate, modelsFrame = completeScaredChildLogisticModFrame, modelType = 'logistic')
hbnScaredParentBinTest = makePreds(testData = hbnScaredParentTestTemplate, modelsFrame = completeScaredParentLogisticModFrame, modelType = 'logistic')

hbnKsadsTest = makePreds(testData = hbnKsadsTest, modelsFrame = completeKsadsLogisticModFrame, modelType = 'logistic')

```


# Permutation tests

Here, run permutation tests for Q2 for the SCARED-P/SCARED-C regression models, as well as log loss and AUC for KSADS logistic models. 

## Set up which columns to permute for each outcome
```{r}
predColsScaredChild = list('sum' = hbnScaredChildTest$sumPreds, 
                           'indiv' = hbnScaredChildTest$indivPreds,
                           'noGi' = hbnScaredChildTest$noGiPreds,
                           'intercept' = hbnScaredChildTest$interceptPreds)

predColsScaredParent = list('sum' = hbnScaredParentTest$sumPreds, 
                           'indiv' = hbnScaredParentTest$indivPreds,
                           'noGi' = hbnScaredParentTest$noGiPreds,
                           'intercept' = hbnScaredParentTest$interceptPreds)


predColsScaredBinChild = list('sum' = hbnScaredChildBinTest$sumPreds, 
                           'indiv' = hbnScaredChildBinTest$indivPreds,
                           'noGi' = hbnScaredChildBinTest$noGiPreds,
                           'intercept' = hbnScaredChildBinTest$interceptPreds)

predColsScaredBinParent = list('sum' = hbnScaredParentBinTest$sumPreds, 
                           'indiv' = hbnScaredParentBinTest$indivPreds,
                           'noGi' = hbnScaredParentBinTest$noGiPreds,
                           'intercept' = hbnScaredParentBinTest$interceptPreds)


predColsKsads = list('sum' = hbnKsadsTest$sumPreds, 
                           'indiv' = hbnKsadsTest$indivPreds,
                           'noGi' = hbnKsadsTest$noGiPreds,
                           'intercept' = hbnKsadsTest$interceptPreds)
```

## Run permutations for each metric and outcome

```{r}
permQ2Child = permute(numPerms = nPerms, trueOutcome = hbnScaredChildTest$scaredSumChild, 
        predCols = predColsScaredChild,
        metric = 'q2')

permQ2Parent = permute(numPerms = nPerms, trueOutcome = hbnScaredParentTest$scaredSumParent, 
        predCols = predColsScaredParent,
        metric = 'q2')


permLogLossKsads = permute(numPerms = nPerms, trueOutcome = hbnKsadsTest$ksadsBin,
                           predCols = predColsKsads,
                           metric = 'crossEntropy')

permAucKsads = permute(numPerms = nPerms, trueOutcome = hbnKsadsTest$ksadsBin,
                           predCols = predColsKsads,
                           metric = 'auc')


permQ2Child$reporter = 'Child'
permQ2Parent$reporter = 'Parent'
```


## Aggregate summaries of permuted outcomes
```{r}
# best permuted distribution for comparison
# the bestPermute() function finds the permuted distribution with the null permuted model (GI Sum, GI Indiv. Items, or No-GI that has the best median performance as a baseline for comparison to ensure that all models are being compared to the same baseline)
permQ2Child = bestPermute(permQ2Child, metric = 'q2')
permQ2Parent = bestPermute(permQ2Parent, metric = 'q2')
permLogLossKsads = bestPermute(permLogLossKsads, metric = 'crossEntropy')
permAucKsads = bestPermute(permAucKsads, metric = 'auc')


# put permutation results in long form
permQ2Long = rbind(permQ2Child, permQ2Parent) %>%
  tidyr::gather(., key = 'model', value = 'q2', -index, -reporter) %>%
  mutate(., model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))



# long form for KSADS log loss
permLogLossLong = permLogLossKsads%>%
  tidyr::gather(., key = 'model', value = 'logLoss', -index) %>%
  mutate(.,
  model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))


# long form for KSADS auc
permAucLong = permAucKsads %>%
  tidyr::gather(., key = 'model', value = 'auc', -index) %>%
  mutate(., model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))
```


# Bootstrapping

  * For SCARED-P/SCARED-C: Q2, RMSE
  * For KSADS: Log loss/AUC

```{r}
# q2 (SCARED)
bootQ2Child = boots(numBoots = nBoots, trueOutcome = hbnScaredChildTest$scaredSumChild, 
        predCols = predColsScaredChild,
        metric = 'q2')

bootQ2Parent = boots(numBoots = nBoots, trueOutcome = hbnScaredParentTest$scaredSumParent, 
        predCols = predColsScaredParent,
        metric = 'q2')

# rmse (SCARED)
bootRMSEChild = boots(numBoots = nBoots, trueOutcome = hbnScaredChildTest$scaredSumChild, 
        predCols = predColsScaredChild,
        metric = 'rmse')

bootRMSEParent = boots(numBoots = nBoots, trueOutcome = hbnScaredParentTest$scaredSumParent, 
        predCols = predColsScaredParent,
        metric = 'rmse')

# log los (SCARED/KSADS)
bootLogLossKsads = boots(numBoots = nBoots, trueOutcome = hbnKsadsTest$ksadsBin, 
        predCols = predColsKsads,
        metric = 'crossEntropy')

bootLogLossChild = boots(numBoots = nBoots, trueOutcome = hbnScaredChildBinTest$scaredBinChild, 
        predCols = predColsScaredBinChild,
        metric = 'crossEntropy')

bootLogLossParent = boots(numBoots = nBoots, trueOutcome = hbnScaredParentBinTest$scaredBinParent, 
        predCols = predColsScaredBinParent,
        metric = 'crossEntropy')


# auc (SCARED/KSADS)
bootAucKsads = boots(numBoots = nBoots, trueOutcome = hbnKsadsTest$ksadsBin, 
        predCols = predColsKsads,
        metric = 'auc')

bootAucChild = boots(numBoots = nBoots, trueOutcome = hbnScaredChildBinTest$scaredBinChild, 
        predCols = predColsScaredBinChild,
        metric = 'auc')

bootAucParent = boots(numBoots = nBoots, trueOutcome = hbnScaredParentBinTest$scaredBinParent, 
        predCols = predColsScaredBinParent,
        metric = 'auc')


# Label who the reporter is
bootQ2Child$reporter = 'Child'
bootQ2Parent$reporter = 'Parent'
bootRMSEChild$reporter = 'Child'
bootRMSEParent$reporter = 'Parent'
bootLogLossChild$reporter = 'Child'
bootAucChild$reporter = 'Child'
bootLogLossParent$reporter = 'Parent'
bootAucParent$reporter = 'Parent'
```

## Aggregate bootstraps to long form and summaries
```{r}
bootQ2Long = rbind(bootQ2Child, bootQ2Parent) %>%
  tidyr::gather(., key = 'model', value = 'q2', -index, -reporter) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))


bootRMSELong = rbind(bootRMSEChild, bootRMSEParent) %>%
  tidyr::gather(., key = 'model', value = 'RMSE', -index, -reporter) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))


bootLogLossKsadsLong = bootLogLossKsads %>%
  tidyr::gather(., key = 'model', value = 'logLoss', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))

bootAucKsadsLong = bootAucKsads %>%
  tidyr::gather(., key = 'model', value = 'auc', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))

# pull together child/parent auc/log loss info for logistic models on SCARED
aucParentChildBinComplete = rbind(bootAucChild, bootAucParent) %>%  
  tidyr::gather(., key = 'model', value = 'auc', -index, -reporter) 

logLossParentChildBinComplete = rbind(bootLogLossChild, bootLogLossParent) %>%  
  tidyr::gather(., key = 'model', value = 'logLoss', -index, -reporter)

# Compile validation summary for binary outcomes for child/parent SCARED
validationSummaryParentChildBinComplete = left_join(aucParentChildBinComplete, logLossParentChildBinComplete) %>%
  tidyr::gather(., key = 'metric', value = 'score', -index, -reporter, -model) %>%
  group_by(reporter, model, metric) %>%
  summarise(lwr95 = quantile(score, .025),
            upr95 = quantile(score, .975),
            median = median(score),
            lwr80 = quantile(score, .1),
            upr80 = quantile(score, .9))

# summary for q2 outcome (SCARED)
bootQ2Summary = bootQ2Long %>%
  group_by(reporter, model) %>%
  summarise(lwr95 = quantile(q2, .025),
            upr95 = quantile(q2, .975),
            median = median(q2),
            lwr80 = quantile(q2, .1),
            upr80 = quantile(q2, .9))


# summary for rmse outcome (SCARED)
validationSummaryRMSECompleteCases = bootRMSELong %>%
  group_by(reporter, model) %>%
  summarise(lwr95 = quantile(RMSE, .025),
            upr95 = quantile(RMSE, .975),
            median = median(RMSE),
            lwr80 = quantile(RMSE, .1),
            upr80 = quantile(RMSE, .9))

# Take out intercept-only model for plotting flat violin of bootstraps
bootQ2Long = dplyr::filter(bootQ2Long, model != 'Intercept Only')

# summary for log loss outcome (KSADS)
bootLogLossSummary = bootLogLossKsadsLong %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(logLoss, .025),
            upr95 = quantile(logLoss, .975),
            median = median(logLoss),
            lwr80 = quantile(logLoss, .1),
            upr80 = quantile(logLoss, .9))

# summary for auc outcome (KSADS)
bootAucSummary = bootAucKsadsLong %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(auc, .025),
            upr95 = quantile(auc, .975),
            median = median(auc),
            lwr80 = quantile(auc, .1),
            upr80 = quantile(auc, .9))
```


# Plots
```{r}
# reorder child/parent for plotting
bootQ2Long = mutate(bootQ2Long, reporter = factor(reporter, levels = c('Parent', 'Child')))
bootQ2Summary = bootQ2Summary %>%
  ungroup() %>%
  mutate(., reporter = factor(reporter, levels = c('Parent', 'Child')))
permQ2Long = mutate(permQ2Long, reporter = factor(reporter, levels = c('Parent', 'Child')))


# Plot of q2 outcomes for SCARED  
bootPlotChildParent = ggplot(bootQ2Long, aes(color = model)) + 
  geom_hline(yintercept = 0, lty = 2) +
  geom_errorbar(data = bootQ2Summary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1, alpha = .7) +
  geom_errorbar(data = bootQ2Summary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1, alpha = .7) +
  geom_point(data = bootQ2Summary, aes(x = model, y = median)) +
  geom_flat_violin(data = permQ2Long, aes(x = model, y = q2), position = position_nudge(x = .1, y = 0), color = 'grey', fill = 'grey', alpha = .7) +
  geom_flat_violin(aes(x = model, y = q2, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'A', subtitle = 'SCARED Child & Parent Report', y = bquote(~q^2), x = '') +
  facet_grid(~reporter) +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal3) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))


bootPlotChildParent

# plot of KSADS log loss
bootPlotKsadsLogLoss = ggplot(bootLogLossKsadsLong, aes(color = model)) + 
  geom_errorbar(data = bootLogLossSummary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1) +
  geom_errorbar(data = bootLogLossSummary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = bootLogLossSummary, aes(x = model, y = median)) +
  geom_flat_violin(data = permLogLossLong, aes(x = model, y = logLoss), position = position_nudge(x = .1, y = 0), fill = 'grey', color = 'grey', alpha = .7) +
  geom_flat_violin(aes(x = model, y = logLoss, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'C', subtitle = 'Clinician Consensus', y = 'Log Loss', x = '') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal4) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))

# plot of KSADS AUC
bootPlotKsadsAuc = ggplot(bootAucKsadsLong, aes(color = model)) + 
  geom_hline(yintercept = .5, lty = 2) + 
  geom_errorbar(data = bootAucSummary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1) +
  geom_errorbar(data = bootAucSummary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = bootAucSummary, aes(x = model, y = median)) +
  geom_flat_violin(data = permAucLong, aes(x = model, y = auc), position = position_nudge(x = .1, y = 0), fill = 'grey', color = 'grey', alpha = .7) +
  geom_flat_violin(aes(x = model, y = auc, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'B', subtitle = 'Clinician Consensus', y = 'AUC', x = '') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal4) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))


bootPlotKsadsLogLoss
bootPlotKsadsAuc
```

# ROC curve plots

Generate ROC curves for each model, then format them all on the same plot

```{r}
rocSum <- roc(hbnKsadsTest$ksadsBin,hbnKsadsTest$sumPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, boot.n=100000, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)

rocIndiv <- roc(hbnKsadsTest$ksadsBin,hbnKsadsTest$indivPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)

rocNoGi <- roc(hbnKsadsTest$ksadsBin,hbnKsadsTest$noGiPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)

rocIntercept <- roc(hbnKsadsTest$ksadsBin,hbnKsadsTest$interceptPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)


# put all roc objects in a list
rocList = list('GI Sum' = rocSum, 'GI Indiv. Items' = rocIndiv, 'Intercept Only' = rocIntercept, 'No GI' = rocNoGi)


# use ggroc() function to plot ROC curves in ggplot!
rocPlot = ggroc(rocList) +
  geom_abline(intercept = 1, slope = 1, lty = 2) +
  labs(title = 'D', subtitle = 'Clinician Consensus - ROC curves') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'right', legend.title = element_blank()) +
  labs(x = 'Specificity', y = 'Sensitivity') +
  scale_color_manual(values = myPal4_reorder, labels = c('GI Sum', 'GI Indiv. Items', 'Intercept Only', 'No GI'))
  
rocPlot
```

# Put it all together on one plot
```{r}
pdf('../plots/hbnCompleteBootstrapPlotAllOutcomesWithIntercept.pdf', height = 4, width = 8)
grid.arrange(bootPlotChildParent, bootPlotKsadsAuc, bootPlotKsadsLogLoss, rocPlot, layout_matrix = rbind(c(1,1,2,3), c(1,1,4, 4)))
dev.off()
```


# Generate model validation summaries with P values 

## P values for Q2 metric

```{r}
# actual Q2 scores
scaredChildQ2Sum = q2(hbnScaredChildTest$sumPreds, hbnScaredChildTest$scaredSumChild)
scaredChildQ2Indiv = q2(hbnScaredChildTest$indivPreds, hbnScaredChildTest$scaredSumChild)
scaredChildQ2NoGI = q2(hbnScaredChildTest$noGiPreds, hbnScaredChildTest$scaredSumChild)
scaredChildQ2Intercept = q2(hbnScaredChildTest$interceptPreds, hbnScaredChildTest$scaredSumChild)
scaredParentQ2Sum = q2(hbnScaredParentTest$sumPreds, hbnScaredParentTest$scaredSumParent)
scaredParentQ2Indiv = q2(hbnScaredParentTest$indivPreds, hbnScaredParentTest$scaredSumParent)
scaredParentQ2NoGI = q2(hbnScaredParentTest$noGiPreds, hbnScaredParentTest$scaredSumParent)
scaredParentQ2Intercept = q2(hbnScaredParentTest$interceptPreds, hbnScaredParentTest$scaredSumParent)

# null vectors
nullQ2Child = permQ2Child$sum
nullQ2Parent = permQ2Parent$sum

# make new dataframe object for the Q2 validation summary
validationSummaryQ2 = bootQ2Summary

# Put Q2 p-values into validation summary dataframe

# Child Q2 p-values
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'GI Sum'] = 
  (sum(nullQ2Child  > scaredChildQ2Sum)+1)/(length(nullQ2Child)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'GI Indiv. Items'] = 
  (sum(nullQ2Child  > scaredChildQ2Indiv)+1)/(length(nullQ2Child)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'No GI'] = 
  (sum(nullQ2Child  > scaredChildQ2NoGI)+1)/(length(nullQ2Child)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'Intercept Only'] = 
  (sum(nullQ2Child  > scaredChildQ2Intercept)+1)/(length(nullQ2Child)+1)

## Parent Q2 p-values
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'GI Sum'] = 
  (sum(nullQ2Parent  > scaredParentQ2Sum)+1)/(length(nullQ2Parent)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'GI Indiv. Items'] = 
  (sum(nullQ2Parent  > scaredParentQ2Indiv)+1)/(length(nullQ2Parent)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'No GI'] = 
  (sum(nullQ2Parent  > scaredParentQ2NoGI)+1)/(length(nullQ2Parent)+1)
validationSummaryQ2$pValNull[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'Intercept Only'] = 
  (sum(nullQ2Parent  > scaredParentQ2Intercept)+1)/(length(nullQ2Parent)+1)

# Q2 Compared to No GI Model
validationSummaryQ2$pValNoGI[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'GI Sum']  = 
  (sum(bootQ2Child$sum < bootQ2Child$noGi)+1)/(nrow(bootQ2Child)+1)
validationSummaryQ2$pValNoGI[validationSummaryQ2$reporter == 'Child' & validationSummaryQ2$model == 'GI Indiv. Items'] = 
  (sum(bootQ2Child$indiv < bootQ2Child$noGi)+1)/(nrow(bootQ2Child)+1)
validationSummaryQ2$pValNoGI[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'GI Sum']  = 
  (sum(bootQ2Parent$sum < bootQ2Parent$noGi)+1)/(nrow(bootQ2Parent)+1)
validationSummaryQ2$pValNoGI[validationSummaryQ2$reporter == 'Parent' & validationSummaryQ2$model == 'GI Indiv. Items'] = 
  (sum(bootQ2Parent$indiv < bootQ2Parent$noGi)+1)/(nrow(bootQ2Parent)+1)

validationSummaryQ2
```

## AUC/Log Loss Validation Summaries with p-values (KSADS)

```{r}
validationSummaryAUC = bootAucSummary
nullAUC = permAucKsads$sum

# p-values over null
validationSummaryAUC$pvalNull[validationSummaryAUC$model == 'GI Sum'] = 
  (sum(nullAUC > validationSummaryAUC$median[validationSummaryAUC$model == 'GI Sum'])+1)/(length(nullAUC)+1)
validationSummaryAUC$pvalNull[validationSummaryAUC$model == 'GI Indiv. Items'] = 
  (sum(nullAUC > validationSummaryAUC$median[validationSummaryAUC$model == 'GI Indiv. Items'])+1)/(length(nullAUC)+1)
validationSummaryAUC$pvalNull[validationSummaryAUC$model == 'No GI'] = 
  (sum(nullAUC > validationSummaryAUC$median[validationSummaryAUC$model == 'No GI'])+1)/(length(nullAUC)+1)
validationSummaryAUC$pvalNull[validationSummaryAUC$model == 'Intercept Only'] = 
  (sum(nullAUC > validationSummaryAUC$median[validationSummaryAUC$model == 'Intercept Only'])+1)/(length(nullAUC)+1)

# p-values over no GI
validationSummaryAUC$pvalNoGi[validationSummaryAUC$model == 'GI Sum'] = (sum(bootAucKsads$sum < bootAucKsads$noGi)+1)/(nrow(bootAucKsads)+1)
validationSummaryAUC$pvalNoGi[validationSummaryAUC$model == 'GI Indiv. Items'] = (sum(bootAucKsads$indiv < bootAucKsads$noGi)+1)/(nrow(bootAucKsads)+1)

validationSummaryAUC
```


## Log loss summaries with p-values (KSADS)

```{r}
validationSummaryLogLoss = bootLogLossSummary
nullLogLoss = permLogLossKsads$sum

# p-values over null
validationSummaryLogLoss$pvalNull[validationSummaryLogLoss$model == 'GI Sum'] = 
  (sum(nullLogLoss < validationSummaryLogLoss$median[validationSummaryLogLoss$model == 'GI Sum']) + 1)/(length(nullLogLoss)+1)
validationSummaryLogLoss$pvalNull[validationSummaryLogLoss$model == 'GI Indiv. Items'] = 
  (sum(nullLogLoss < validationSummaryLogLoss$median[validationSummaryLogLoss$model == 'GI Indiv. Items'])+1)/(length(nullLogLoss)+1)
validationSummaryLogLoss$pvalNull[validationSummaryLogLoss$model == 'No GI'] =
  (sum(nullLogLoss < validationSummaryLogLoss$median[validationSummaryLogLoss$model == 'No GI']) + 1)/(length(nullLogLoss)+1)
validationSummaryLogLoss$pvalNull[validationSummaryLogLoss$model == 'Intercept Only'] = 
  (sum(nullLogLoss < validationSummaryLogLoss$median[validationSummaryLogLoss$model == 'Intercept Only'])+1)/(length(nullLogLoss)+1)


# p-values over no GI
validationSummaryLogLoss$pvalNoGi[validationSummaryLogLoss$model == 'GI Sum'] =
  (sum(bootLogLossKsads$sum > bootLogLossKsads$noGi)+1)/(nrow(bootLogLossKsads)+1)
validationSummaryLogLoss$pvalNoGi[validationSummaryLogLoss$model == 'GI Indiv. Items'] = 
  (sum(bootLogLossKsads$indiv > bootLogLossKsads$noGi)+1)/(nrow(bootLogLossKsads) +1)

validationSummaryLogLoss
```

# Save validation summary outputs for reporting
```{r}
save(validationSummaryQ2, validationSummaryAUC, validationSummaryLogLoss, validationSummaryRMSECompleteCases, validationSummaryParentChildBinComplete, file = '../output/validationSummaryCompleteCases.rda')
```

# Session Info
```{r}
sessionInfo()
```