---
title: "5b: Validation of GI-anxiety models in NYC/LA data  -- 3NN pipeline"
author: "Paul A. Bloom"
date: "September 10, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown calculates validation performance metrics for GI-anxiety models trained on the HBN training data on the HBN holdout data using permutation and bootstrapping ONLY for the SCARED-P metric but for both linear/logistic models. 3NN pipeline.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Load pacakages/Set themes
```{r}
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(pROC)
library(gridExtra)

# Plot theme
mytheme = theme_bw() 
theme_set(mytheme)

# Source code for flat violin plots
source('helperFunctions.R')

# color palette
myPal3 = c('#2b8cbe', '#88419d','#cb181d')
myPal3_reorder = c('#88419d', '#2b8cbe','#cb181d')
myPal4 = c('#2b8cbe', '#88419d', '#238b45','#cb181d')
myPal4_reorder = c('#88419d', '#2b8cbe', '#238b45','#cb181d')

# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

# Number of iterations (will affect runtime)

```{r}
nPerms = 10000
nBoots = 10000
```

## Load in SB/ELFK data for test sets
```{r}
sb = read.csv('../cleanData/sbDataClean.csv', stringsAsFactors = FALSE) 

elfk = read.csv('../cleanData/elfkDataClean.csv', stringsAsFactors = FALSE) 

# rename vars to match HBN
sb = dplyr::select(sb, cbclGISum = CBCL_GI_sum, scaredSumParent = sum_scared, age = bl_age_gi_new, sex = Sex, nausea, stomachache_cramps, constipated, vomiting)
sb$dataset = 'LA'
elfk = dplyr::select(elfk, cbclGISum = CBCL_GI_sum, scaredSumParent = sum_scared, age = bl_age_gi_new, sex = Sex, nausea, stomachache_cramps, constipated, vomiting)
elfk$dataset = 'NYC'

# get mean age from HBN data
meanAge = mean(read.csv('../cleanData/fullHBN.csv', stringsAsFactors = FALSE)$age)

# bind sb and elfk together, get centered ages
sbelfk = rbind(sb, elfk) %>%
  mutate(., ageCenter = age - meanAge)
```


# Load model objects
```{r}
load('../output/scaredParentModels.rda')
```


# Make Predictions On Test Set

Generate predictions for all models trained on the HBN training data
```{r}
# get binned SCARED-P
sbelfk$scaredBinParent = ifelse(sbelfk$scaredSumParent >= 25, 1, 0)

# write out cleaned sb/elfk data
write.csv(sbelfk, file = '../cleanData/sb_elfk.csv', row.names = FALSE)

# Make predictions (linear)
sbelfk = makePreds(testData = sbelfk, modelsFrame = threeNNScaredParentLinearModFrame, modelType = 'linear')

# Make predictions (logistic)
sbelfkLogistic= makePreds(testData = dplyr::select(sbelfk, -contains('pred')), 
                          modelsFrame = threeNNScaredParentLogisticModFrame, modelType = 'logistic')
```

# Permutation tests

Define columns to create null permuted distributions for (i.e. the model predictions)
```{r}
predColsScaredParent = list('sum' = sbelfk$sumPreds, 
                            'indiv' = sbelfk$indivPreds,
                            'noGi' = sbelfk$noGiPreds,
                            'intercept' = sbelfk$interceptPreds)

predColsScaredParentLogistic = list('sum' = sbelfkLogistic$sumPreds, 
                                    'indiv' = sbelfkLogistic$indivPreds,
                                    'noGi' = sbelfkLogistic$noGiPreds,
                                    'intercept' = sbelfkLogistic$interceptPreds)
```

# Run permutations for each metric for both linear/logistic

```{r}
permQ2Parent = permute(numPerms = nPerms, trueOutcome = sbelfk$scaredSumParent, 
                       predCols = predColsScaredParent,
                       metric = 'q2') %>%
  bestPermute(., metric = 'q2')

permAucParent = permute(numPerms = nPerms, trueOutcome = sbelfkLogistic$scaredBinParent, 
                        predCols = predColsScaredParentLogistic,
                        metric = 'auc') %>%
  bestPermute(., metric = 'auc')

permLogLossParent = permute(numPerms = nPerms, trueOutcome = sbelfkLogistic$scaredBinParent, 
                            predCols = predColsScaredParentLogistic,
                            metric = 'crossEntropy') %>%
  bestPermute(., metric = 'crossEntropy')
```

## Aggregate summaries of permuted outcomes
```{r}
permQ2Long = permQ2Parent %>%
  tidyr::gather(., key = 'model', value = 'q2', -index) %>%
  mutate(., model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))

permAucLong = permAucParent %>%
  tidyr::gather(., key = 'model', value = 'auc', -index) %>%
  mutate(., model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))

permLogLossLong = permLogLossParent %>%
  tidyr::gather(., key = 'model', value = 'logLoss', -index) %>%
  mutate(., model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))
```

# Bootstrap

  * Linear: q2 and RMSE
  * Logistic: AUC and Log loss
```{r}
bootQ2Parent = boots(numBoots = nBoots, trueOutcome = sbelfk$scaredSumParent, 
                     predCols = predColsScaredParent,
                     metric = 'q2')

bootRMSEParent = boots(numBoots = nBoots, trueOutcome = sbelfk$scaredSumParent, 
                       predCols = predColsScaredParent,
                       metric = 'rmse')

bootAucParent = boots(numBoots = nBoots, trueOutcome = sbelfkLogistic$scaredBinParent, 
                      predCols = predColsScaredParentLogistic,
                      metric = 'auc')

bootLogLossParent = boots(numBoots = nBoots, trueOutcome = sbelfkLogistic$scaredBinParent, 
                          predCols = predColsScaredParentLogistic,
                          metric = 'crossEntropy')
```

## Aggregate bootstraps for each performance metric to long form

```{r}
bootQ2Long = rbind(bootQ2Parent) %>%
  tidyr::gather(., key = 'model', value = 'q2', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))


bootRMSELong = rbind(bootRMSEParent) %>%
  tidyr::gather(., key = 'model', value = 'RMSE', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))


bootAucLong = rbind(bootAucParent) %>%
  tidyr::gather(., key = 'model', value = 'auc', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))

bootLogLossLong = rbind(bootLogLossParent) %>%
  tidyr::gather(., key = 'model', value = 'logLoss', -index) %>%
  mutate(model = case_when(
    model == 'sum' ~ 'GI Sum',
    model == 'indiv' ~ 'GI Indiv. Items',
    model == 'noGi' ~ 'No GI',
    model == 'intercept' ~ 'Intercept Only'
  ))
```

## Summaries of each performance metric distribution 

```{r}
bootQ2Summary = bootQ2Long %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(q2, .025),
            upr95 = quantile(q2, .975),
            median = median(q2),
            lwr80 = quantile(q2, .1),
            upr80 = quantile(q2, .9))

bootRMSESummary = bootRMSELong %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(RMSE, .025),
            upr95 = quantile(RMSE, .975),
            median = median(RMSE),
            lwr80 = quantile(RMSE, .1),
            upr80 = quantile(RMSE, .9))

bootAucSummary = bootAucLong %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(auc, .025),
            upr95 = quantile(auc, .975),
            median = median(auc),
            lwr80 = quantile(auc, .1),
            upr80 = quantile(auc, .9))

bootLogLossSummary = bootLogLossLong %>%
  group_by(model) %>%
  summarise(lwr95 = quantile(logLoss, .025),
            upr95 = quantile(logLoss, .975),
            median = median(logLoss),
            lwr80 = quantile(logLoss, .1),
            upr80 = quantile(logLoss, .9))

```

# Plot bootstrapped/permuted performance
```{r}
# Q2 for linear
bootPlotSbelfkParent = ggplot(bootQ2Long, aes(color = model)) + 
  geom_hline(yintercept = .0, lty = 2) + 
  geom_errorbar(data = bootQ2Summary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1) +
  geom_errorbar(data = bootQ2Summary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = bootQ2Summary, aes(x = model, y = median)) +  
  geom_flat_violin(data = permQ2Long, aes(x = model, y = q2), position = position_nudge(x = .1, y = 0), alpha = .7, fill = 'grey', color = 'grey') +
  geom_flat_violin(aes(x = model, y = q2, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'A', subtitle = 'SCARED Parent Report\nCombined LA + NYC cohorts', y = bquote(~q^2), x = '') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal4) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))


# AUC for logistic
bootPlotSbelfkParentAuc = ggplot(bootAucLong, aes(color = model)) + 
  geom_hline(yintercept = .5, lty = 2) + 
  geom_errorbar(data = bootAucSummary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1) +
  geom_errorbar(data = bootAucSummary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = bootAucSummary, aes(x = model, y = median)) +  
  geom_flat_violin(data = permAucLong, aes(x = model, y = auc), position = position_nudge(x = .1, y = 0), alpha = .7, color = 'grey', fill = 'grey') +
  geom_flat_violin(aes(x = model, y = auc, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'B', y = 'AUC', x = '') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal4) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))

# Log Loss for logistic
bootPlotSbelfkParentLogLoss = ggplot(bootLogLossLong, aes(color = model)) + 
  geom_errorbar(data = bootLogLossSummary, aes(x = model, ymin = lwr95, ymax = upr95), width = .1) +
  geom_errorbar(data = bootLogLossSummary, aes(x = model, ymin = lwr80, ymax = upr80), width = 0, lwd = 1) +
  geom_point(data = bootLogLossSummary, aes(x = model, y = median)) + 
  geom_flat_violin(data = permLogLossLong, aes(x = model, y = logLoss), position = position_nudge(x = .1, y = 0), alpha = .7, color = 'grey', fill = 'grey') +
  geom_flat_violin(aes(x = model, y = logLoss, fill = model), position = position_nudge(x = .1, y = 0), alpha = .7) +
  labs(title = 'C', y = 'Log Loss', x = '') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 30, hjust = 1),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  scale_fill_manual(values = myPal4) +
  scale_color_manual(values = myPal4) +
  scale_x_discrete(limits = c('GI Sum', 'GI Indiv. Items', 'No GI', 'Intercept Only'))


bootPlotSbelfkParentLogLoss
bootPlotSbelfkParentAuc
bootPlotSbelfkParent
```

# ROC plots

```{r}
rocSum <- roc(sbelfkLogistic$scaredBinParent, sbelfkLogistic$sumPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, boot.n=100000, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)

rocIndiv <- roc(sbelfkLogistic$scaredBinParent,sbelfkLogistic$indivPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)

rocNoGi <- roc(sbelfkLogistic$scaredBinParent,sbelfkLogistic$noGiPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)


rocIntercept <- roc(sbelfkLogistic$scaredBinParent,sbelfkLogistic$interceptPreds,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)


# pull roc plots for each model together
rocList = list('GI Sum' = rocSum, 'GI Indiv. Items' = rocIndiv, 'Intercept Only' = rocIntercept, 'No GI' = rocNoGi)


# plot all roc curves together in one ggplot
rocPlot = ggroc(rocList) +
  geom_abline(intercept = 1, slope = 1, lty = 2) +
  labs(title = 'ROC') +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = 'right', legend.title = element_blank()) +
  labs(x = 'Specificity', y = 'Sensitivity', title = 'D', subtitle = 'ROC curves') +
  scale_color_manual(values = myPal4_reorder, labels = c('GI Sum', 'GI Indiv. Items', 'Intercept Only', 'No GI'))



rocPlot
```

# Multipanel LA/NYC validation plot

```{r}
pdf('../plots/sbelfkHBNPreds3NNScaredBootstrap.pdf', height = 4, width = 8)
grid.arrange(bootPlotSbelfkParent, bootPlotSbelfkParentAuc, bootPlotSbelfkParentLogLoss, rocPlot, layout_matrix = rbind(c(1,1,2,3), c(1,1, 4,4)))
dev.off()

```

# Create validation summary for sb-elfk testing with p-values

```{r}
# actual Q2 scores
scaredParentQ2Sum = q2(sbelfk$sumPreds, sbelfk$scaredSumParent)
scaredParentQ2Indiv = q2(sbelfk$indivPreds, sbelfk$scaredSumParent)
scaredParentQ2NoGI = q2(sbelfk$noGiPreds, sbelfk$scaredSumParent)
scaredParentQ2Intercept = q2(sbelfk$interceptPreds, sbelfk$scaredSumParent)


# null vectors
nullQ2Parent = permQ2Parent$sum
validationSummary3NNSbElfkQ2 = bootQ2Summary

# Q2 p-values over null permuted distribution
validationSummary3NNSbElfkQ2$pValNull[validationSummary3NNSbElfkQ2$model == 'GI Sum'] = 
  (sum(nullQ2Parent  > scaredParentQ2Sum)+1)/(length(nullQ2Parent)+1)
validationSummary3NNSbElfkQ2$pValNull[validationSummary3NNSbElfkQ2$model == 'GI Indiv. Items'] = 
  (sum(nullQ2Parent  > scaredParentQ2Indiv)+1)/(length(nullQ2Parent)+1)
validationSummary3NNSbElfkQ2$pValNull[validationSummary3NNSbElfkQ2$model == 'No GI'] = 
  (sum(nullQ2Parent  > scaredParentQ2NoGI)+1)/((length(nullQ2Parent)+1)+1)
validationSummary3NNSbElfkQ2$pValNull[validationSummary3NNSbElfkQ2$model == 'Intercept Only'] = 
  (sum(nullQ2Parent  > scaredParentQ2Intercept)+1)/(length(nullQ2Parent)+1)

# Q2 p-values for GI models vs. No-GI
validationSummary3NNSbElfkQ2$pValNoGI[validationSummary3NNSbElfkQ2$model == 'GI Sum']  = 
  (sum(bootQ2Parent$sum < bootQ2Parent$noGi)+1)/(nrow(bootQ2Parent)+1)
validationSummary3NNSbElfkQ2$pValNoGI[validationSummary3NNSbElfkQ2$model == 'GI Indiv. Items'] = 
  (sum(bootQ2Parent$indiv < bootQ2Parent$noGi)+1)/(nrow(bootQ2Parent)+1)

validationSummary3NNSbElfkQ2
```

AUC Validation Summary
```{r}
validationSummary3NNSbElfkAUC = bootAucSummary

# null vector
nullAUC = permAucParent$sum

# p-values over null
validationSummary3NNSbElfkAUC$pvalNull[validationSummary3NNSbElfkAUC$model == 'GI Sum'] = 
  (sum(nullAUC > validationSummary3NNSbElfkAUC$median[validationSummary3NNSbElfkAUC$model == 'GI Sum'])+1)/(length(nullAUC)+1)
validationSummary3NNSbElfkAUC$pvalNull[validationSummary3NNSbElfkAUC$model == 'GI Indiv. Items'] = 
  (sum(nullAUC > validationSummary3NNSbElfkAUC$median[validationSummary3NNSbElfkAUC$model == 'GI Indiv. Items'])+1)/(length(nullAUC)+1)
validationSummary3NNSbElfkAUC$pvalNull[validationSummary3NNSbElfkAUC$model == 'No GI'] = 
 (sum(nullAUC > validationSummary3NNSbElfkAUC$median[validationSummary3NNSbElfkAUC$model == 'No GI'])+1)/(length(nullAUC)+1)
validationSummary3NNSbElfkAUC$pvalNull[validationSummary3NNSbElfkAUC$model == 'Intercept Only'] = 
  (sum(nullAUC > validationSummary3NNSbElfkAUC$median[validationSummary3NNSbElfkAUC$model == 'Intercept Only'])+1)/(length(nullAUC)+1)

# p-values of no-GI over GI models (no gi did better here)
validationSummary3NNSbElfkAUC$pvalNoGi[validationSummary3NNSbElfkAUC$model == 'GI Sum'] = 
  (sum(bootAucParent$sum > bootAucParent$noGi)+1)/(nrow(bootAucParent)+1)
validationSummary3NNSbElfkAUC$pvalNoGi[validationSummary3NNSbElfkAUC$model == 'GI Indiv. Items'] = 
  (sum(bootAucParent$indiv > bootAucParent$noGi)+1)/(nrow(bootAucParent)+1)

validationSummary3NNSbElfkAUC
```

Log Loss Validation Summary

```{r}
validationSummary3NNSbElfkLogLoss = bootLogLossSummary

# null vector
nullLogLoss = permLogLossParent$sum


# p-values over null
validationSummary3NNSbElfkLogLoss$pvalNull[validationSummary3NNSbElfkLogLoss$model == 'GI Sum'] = 
  (sum(nullLogLoss < validationSummary3NNSbElfkLogLoss$median[validationSummary3NNSbElfkLogLoss$model == 'GI Sum'])+1)/(length(nullLogLoss) +1)
validationSummary3NNSbElfkLogLoss$pvalNull[validationSummary3NNSbElfkLogLoss$model == 'GI Indiv. Items'] = 
  (sum(nullLogLoss < validationSummary3NNSbElfkLogLoss$median[validationSummary3NNSbElfkLogLoss$model == 'GI Indiv. Items'])+1)/(length(nullLogLoss) +1)
validationSummary3NNSbElfkLogLoss$pvalNull[validationSummary3NNSbElfkLogLoss$model == 'No GI'] = 
  (sum(nullLogLoss < validationSummary3NNSbElfkLogLoss$median[validationSummary3NNSbElfkLogLoss$model == 'No GI'])+1)/(length(nullLogLoss) +1)
validationSummary3NNSbElfkLogLoss$pvalNull[validationSummary3NNSbElfkLogLoss$model == 'Intercept Only'] = 
  (sum(nullLogLoss < validationSummary3NNSbElfkLogLoss$median[validationSummary3NNSbElfkLogLoss$model == 'Intercept Only'])+1)/(length(nullLogLoss) +1)


# p-values over no GI
validationSummary3NNSbElfkLogLoss$pvalNoGi[validationSummary3NNSbElfkLogLoss$model == 'GI Sum'] = 
  (sum(bootLogLossParent$sum > bootLogLossParent$noGi)+1)/(nrow(bootLogLossParent)+1)
validationSummary3NNSbElfkLogLoss$pvalNoGi[validationSummary3NNSbElfkLogLoss$model == 'GI Indiv. Items'] = 
  (sum(bootLogLossParent$indiv > bootLogLossParent$noGi)+1)/(nrow(bootLogLossParent)+1)


validationSummary3NNSbElfkLogLoss

```

# Save validation summary outputs for reporting
```{r}
validationSummary3NNSbElfkRMSE = bootRMSESummary
save(validationSummary3NNSbElfkQ2, validationSummary3NNSbElfkAUC, validationSummary3NNSbElfkLogLoss, validationSummary3NNSbElfkRMSE, file = '../output/validationSummarySbElfk3NN.rda')
```

# Session Info
```{r}
sessionInfo()
```