---
title: "6: Compare Validation Summaries Across Metrics, Pipelines, Outcomes and Holdout Sets"
author: "Paul A. Bloom"
date: "January 23, 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown creates plots visualizing model validation performance across metrics, pipelines, outcomes, and holdout sets. It generates one plot for performance on the HBN holdout data and one for performance on the SB + ELFK combined data.

  * Metrics: Q2, RMSE, Log Loss, AUC
  * Pipelines: Complete Cases, 3NN, 9NN
  * Outcomes: SCARED-P (continuous/binary), SCARED-C (continuous/binary), KSADS (binary)


```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(cowplot)
theme_set(theme_bw())

# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

# Load HBN holdout validation summaries
```{r}
load('../output/validationSummary3NN.rda')
load('../output/validationSummary9NN.rda')
load('../output/validationSummaryCompleteCases.rda')
```

# Clean HBN validation summaries

## SCARED Binary Outcomes (log loss / auc)

Rename models and pipelines here in each summary dataframe
```{r}
validationSummaryParentChildBinComplete = validationSummaryParentChildBinComplete %>%
  ungroup() %>%
  mutate(., 
         model = case_when(
          model == 'sum' ~ 'GI Sum',
          model == 'indiv' ~ 'GI Indiv. Items',
          model == 'noGi' ~ 'No GI',
          model == 'intercept' ~ 'Intercept Only'
        ),
        Pipeline = 'Complete Cases')

validationSummary3NNParentChildBinComplete = validationSummary3NNParentChildBinComplete %>%
  ungroup() %>%
  mutate(., 
         model = case_when(
          model == 'sum' ~ 'GI Sum',
          model == 'indiv' ~ 'GI Indiv. Items',
          model == 'noGi' ~ 'No GI',
          model == 'intercept' ~ 'Intercept Only'
        ),
        Pipeline = '3NN Imputation')


validationSummary9NNParentChildBinComplete = validationSummary9NNParentChildBinComplete %>%
  ungroup() %>%
  mutate(., 
         model = case_when(
          model == 'sum' ~ 'GI Sum',
          model == 'indiv' ~ 'GI Indiv. Items',
          model == 'noGi' ~ 'No GI',
          model == 'intercept' ~ 'Intercept Only'
        ),
        Pipeline = '9NN Imputation')
```


## SCARED Q2 summaries

Label with pipeline, metric, holdout set
```{r}
validationSummaryQ2 =  validationSummaryQ2 %>%
  mutate(., Pipeline = 'Complete Cases', `Holdout Set` = 'HBN Holdout', Metric = 'Q2')

validationSummary3NNQ2 =  validationSummary3NNQ2 %>%
  mutate(., Pipeline = '3NN Imputation', `Holdout Set` = 'HBN Holdout', Metric = 'Q2')

validationSummary9NNQ2 =  validationSummary9NNQ2 %>%
  mutate(., Pipeline = '9NN Imputation', `Holdout Set` = 'HBN Holdout', Metric = 'Q2')

# Pull all q2 metrics together across pipelines
allQ2 = plyr::rbind.fill(validationSummaryQ2, validationSummary3NNQ2, validationSummary9NNQ2)

# order factor for reporter
allQ2= mutate(allQ2, reporter = factor(reporter, levels = c('Parent', 'Child', 'Clinician Consensus')))
```

## RMSE summaries 
```{r}
validationSummaryRMSECompleteCases$Pipeline = 'Complete Cases'
validationSummary3NNRMSE$Pipeline = '3NN Imputation'
validationSummary9NNRMSE$Pipeline = '9NN Imputation'

# pull rmse summaries together across pipelines
allRMSE = rbind(validationSummaryRMSECompleteCases, validationSummary3NNRMSE, validationSummary9NNRMSE) %>%
  ungroup()

# reorder factor for reporter
allRMSE= mutate(allRMSE, reporter = factor(reporter, levels = c('Parent', 'Child', 'Clinician Consensus')))

```

## AUC summaries 

```{r}
# Clean KSADS AUC summaries
validationSummaryAUC =  validationSummaryAUC %>%
  mutate(., Pipeline = 'Complete Cases', 
         `Holdout Set` = 'HBN Holdout', 
         Metric = 'AUC', 
         reporter = 'Clinician Consensus')

validationSummary3NNAUC =  validationSummary3NNAUC %>%
  mutate(., Pipeline = '3NN Imputation',
         `Holdout Set` = 'HBN Holdout', 
         Metric = 'AUC', 
         reporter = 'Clinician Consensus')

validationSummary9NNAUC =  validationSummary9NNAUC %>%
  mutate(., Pipeline = '9NN Imputation', 
         `Holdout Set` = 'HBN Holdout', 
         Metric = 'AUC', 
         reporter = 'Clinician Consensus')

# Pull AUC summaries together across outcomes and pipelines 
allAUC = plyr::rbind.fill(validationSummaryAUC, validationSummary3NNAUC, validationSummary9NNAUC,
                          data.frame(dplyr::filter(validationSummaryParentChildBinComplete, metric == 'auc')),
                          data.frame(dplyr::filter(validationSummary3NNParentChildBinComplete, metric == 'auc')),
                          data.frame(dplyr::filter(validationSummary9NNParentChildBinComplete, metric == 'auc')))

allAUC= mutate(allAUC, reporter = factor(reporter, levels = c('Parent', 'Child', 'Clinician Consensus')))
```

## Log Loss Summaries
```{r}
validationSummaryLogLoss =  validationSummaryLogLoss %>%
  mutate(., Pipeline = 'Complete Cases', `Holdout Set` = 'HBN Holdout', 
         Metric = 'Log Loss', reporter = 'Clinician Consensus')

validationSummary3NNLogLoss =  validationSummary3NNLogLoss %>%
  mutate(., Pipeline = '3NN Imputation', `Holdout Set` = 'HBN Holdout', 
         Metric = 'Log Loss', reporter = 'Clinician Consensus')

validationSummary9NNLogLoss =  validationSummary9NNLogLoss %>%
  mutate(., Pipeline = '9NN Imputation', `Holdout Set` = 'HBN Holdout', 
         Metric = 'Log Loss', reporter = 'Clinician Consensus')

# Pull log loss summaries together across pipelines and for child/parent
allLogLoss = plyr::rbind.fill(validationSummaryLogLoss, 
                              validationSummary3NNLogLoss, 
                              validationSummary9NNLogLoss,
                              data.frame(dplyr::filter(validationSummaryParentChildBinComplete, metric == 'logLoss')),
                              data.frame(dplyr::filter(validationSummary3NNParentChildBinComplete,metric == 'logLoss')),
                              data.frame(dplyr::filter(validationSummary9NNParentChildBinComplete, metric == 'logLoss')))

# rename reporter
allLogLoss = mutate(allLogLoss, reporter = factor(reporter, levels = c('Parent', 'Child', 'Clinician Consensus')))
```

# Plot summaries of each metric
```{r}
# Q2 for SCARED-P and SCARED-C
q2plot = ggplot(allQ2, aes(x = model, y = median, color = Pipeline)) +
  facet_grid(~reporter, drop = TRUE, space = 'free') +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15)) +
  labs(y = bquote(~q^2), x = '', title = 'A', subtitle = 'Continuous Anxiety Symptoms')

# RMSE for SCARED-P and SCARED-C
rmsePlot =  ggplot(allRMSE, aes(x = model, y = median, color = Pipeline)) +
  facet_grid(~reporter, drop = TRUE, space = 'free') +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15),legend.position = 'none') +
  labs(y = 'RMSE', x = '', title = 'B', subtitle = 'Continuous Anxiety Symptoms')

rmsePlot

# AUC for all outcomes 
aucPlot = ggplot(allAUC, aes(x = model, y = median, color = Pipeline)) +
  facet_grid(~reporter) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15), 
        legend.position = 'none') +
  labs(y = 'AUC', x = '', title = 'C', subtitle = 'Clinical Cutoff / Diagnoses')

aucPlot

# Log loss for all outcomes
logLossPlot = ggplot(allLogLoss, aes(x = model, y = median, color = Pipeline)) +
  facet_grid(~reporter) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15), 
        legend.position = 'none') +
  labs(y = 'Log Loss', x = '', title = 'D', subtitle = 'Clinical Cutoff / Diagnoses')


logLossPlot


```

## Multipanel plot summarizing validation results across pipelines, metrics, and outcomes on HBN holdout data

```{r}
pdf('../plots/suppValidationComparison.pdf', height = 10, width = 8)
grid.arrange(q2plot, rmsePlot, aucPlot, logLossPlot, layout_matrix = rbind(c(1,1), c(2,2), c(3,3), c(4,4)))
dev.off()
```

# SB / ELFK validation summaries

SCARED-P only for SB/ELFK

```{r}
# load in summaries
load('../output/validationSummarySbElfkCompleteCases.rda')
load('../output/validationSummarySbElfk3NN.rda')
load('../output/validationSummarySbElfk9NN.rda')
```


# Clean summaries

Label which pipeline they come from 
```{r}
# q2
validationSummarySbElfkQ2 =  validationSummarySbElfkQ2 %>%
  mutate(., Pipeline = 'Complete Cases')

validationSummary3NNSbElfkQ2=  validationSummary3NNSbElfkQ2 %>%
  mutate(., Pipeline = '3NN Imputation')

validationSummary9NNSbElfkQ2=  validationSummary9NNSbElfkQ2 %>%
  mutate(., Pipeline = '9NN Imputation')

# rmse
validationSummarySbElfkRMSE =  validationSummarySbElfkRMSE %>%
  mutate(., Pipeline = 'Complete Cases')

validationSummary3NNSbElfkRMSE=  validationSummary3NNSbElfkRMSE %>%
  mutate(., Pipeline = '3NN Imputation')

validationSummary9NNSbElfkRMSE=  validationSummary9NNSbElfkRMSE %>%
  mutate(., Pipeline = '9NN Imputation')

# AUC
validationSummarySbElfkAUC =  validationSummarySbElfkAUC %>%
  mutate(., Pipeline = 'Complete Cases')

validationSummary3NNSbElfkAUC=  validationSummary3NNSbElfkAUC %>%
  mutate(., Pipeline = '3NN Imputation')

validationSummary9NNSbElfkAUC=  validationSummary9NNSbElfkAUC %>%
  mutate(., Pipeline = '9NN Imputation')

# Log loss
validationSummarySbElfkLogLoss =  validationSummarySbElfkLogLoss %>%
  mutate(., Pipeline = 'Complete Cases')

validationSummary3NNSbElfkLogLoss=  validationSummary3NNSbElfkLogLoss %>%
  mutate(., Pipeline = '3NN Imputation')

validationSummary9NNSbElfkLogLoss=  validationSummary9NNSbElfkLogLoss %>%
  mutate(., Pipeline = '9NN Imputation')

```

## For each outcome, bind together across pipelines

```{r}
sbelfkQ2 = rbind(validationSummarySbElfkQ2, validationSummary3NNSbElfkQ2, validationSummary9NNSbElfkQ2)
sbelfkRMSE = rbind(validationSummarySbElfkRMSE, validationSummary3NNSbElfkRMSE, validationSummary9NNSbElfkRMSE)
sbelfkAUC = rbind(validationSummarySbElfkAUC, validationSummary3NNSbElfkAUC, validationSummary9NNSbElfkAUC)
sbelfkLogLoss = rbind(validationSummarySbElfkLogLoss, validationSummary3NNSbElfkLogLoss, validationSummary9NNSbElfkLogLoss)

```

## SB/ELFK plots for each outcome
```{r}
# Q2
q2sbelfk = ggplot(sbelfkQ2, aes(x = model, y = median, color = Pipeline)) +
  geom_hline(yintercept = 0, lty = 2) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) 

# pull out legend to put it at the bottom of the plot
legend = get_legend(q2sbelfk + 
                      theme(legend.position = "bottom", 
                            legend.justification="center", 
                            legend.title = element_blank()))

# reomve legend specifically from Q2 plot (legend will be at the bottom of multipanel plot instead)
q2sbelfk = q2sbelfk +  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15), 
        legend.position = 'none') +
  labs(y = bquote(~q^2), x = '', title = 'A', subtitle = 'Continuous Anxiety Symptoms')

# Q2
RMSEsbelfk = ggplot(sbelfkRMSE, aes(x = model, y = median, color = Pipeline)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15), 
        legend.position = 'none') +
  labs(y = 'RMSE', x = '', title = 'B', subtitle = 'Continuous Anxiety Symptoms')

# AUC
AUCsbelfk = ggplot(sbelfkAUC, aes(x = model, y = median, color = Pipeline)) +
  geom_hline(yintercept = 0.5, lty = 2) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15),
        legend.position = 'none') +
  labs(y = 'AUC', x = '', title = 'C', subtitle = 'Clinical Cutoff')


# Log Loss
LogLosssbelfk = ggplot(sbelfkLogLoss, aes(x = model, y = median, color = Pipeline)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_errorbar(aes(ymin = lwr95, ymax = upr95), width = 0, position = position_dodge(width = .2)) +
  theme(axis.text.x = element_text(angle =45, hjust = 1, size = 8), 
        plot.title = element_text(hjust = 0, size = 15),
        legend.position = 'none') +
  labs(y = 'Log Loss', x = '', title = 'D', subtitle = 'Clinical Cutoff')

q2sbelfk
RMSEsbelfk
AUCsbelfk
LogLosssbelfk
```

## Multipanel SB + ELFK validation plot
```{r}
sbelfkValGrid = plot_grid(q2sbelfk,RMSEsbelfk, AUCsbelfk, LogLosssbelfk, legend, ncol = 2, rel_heights = c(1,1,.1))
save_plot(sbelfkValGrid, file = '../plots/suppValidationComparisonSB_ELFK.pdf', base_height = 8, base_width = 8)
```

# Session Info
```{r}
sessionInfo()
```