---
title: "9: Analyses of based on age, sex, and eca"
author: "Paul A. Bloom"
date: "January 22, 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: paper
---

This markdown generates plots and models for our main predictors and outcomes (GI and anxiety) as a function of age, sex, and early caregiving adversity. These analyses are mostly for the supplemental.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(ggpubr)
library(rstanarm)
library(cowplot)
source('helperFunctions.R')
myPal3 = c('#2b8cbe', '#88419d','#cb181d')

# Plot theme
mytheme = theme_bw() 
theme_set(mytheme)

# To get the same random number generator across R versions (https://blog.revolutionanalytics.com/2019/05/whats-new-in-r-360.html)
if (as.numeric(R.Version()$major) >= 3 & as.numeric(R.Version()$minor) >= 6.0){ 
  RNGkind(sample.kind="Rounding")
}
```

# Clean data from all three cohorts
```{r ELFK & SB Samples, echo=FALSE, warning=FALSE, message=FALSE}
allHbn = read.csv('../cleanData/fullHBN.csv')
sb = read.csv('../cleanData/sbDataClean.csv', stringsAsFactors = FALSE)
elfk = read.csv('../cleanData/elfkDataClean.csv', stringsAsFactors = FALSE)

elfk = dplyr::select(elfk, -time1_scared_11removed_average)
elfk$Cohort = 'NYC'
sb$Cohort = 'LA'

# Combine SB and elfk
sbElfk = rbind(sb, elfk) %>%
  dplyr::select(., scaredSumParent = sum_scared, id = SUBID, scaredBinParent = scaredBin, age = bl_age_gi_new, pi = International_adoption, Sex, cbclGISum = CBCL_GI_sum, nausea, stomachache_cramps, constipated, vomiting, Cohort)

hbnDescrip = dplyr::select(allHbn, Sex = sex, id = Identifiers, everything()) %>%
  mutate(., Cohort = 'HBN')

# Combine all three datasets
allDescrip = plyr::rbind.fill(hbnDescrip, sbElfk) %>%
    dplyr::select(., Age = age, everything())
```


# Make histograms for GI/scaredP

```{r}
giHist = ggplot(allDescrip) + geom_histogram(aes(cbclGISum, fill = Cohort), bins = 9) +
  facet_wrap('Cohort', scales = 'free_y') + 
  scale_color_brewer(palette = 'Set1') +
  scale_fill_brewer(palette = 'Set1') +
  theme(legend.position = 'none') +
  labs(x = '', title = 'A', subtitle = 'CBCL GI Sum Score', y = 'Count') +
  scale_x_continuous(breaks = 0:8) +
  theme(panel.grid.minor = element_blank(), panel.grid.major.y = element_blank())

giHist

scaredPHist = ggplot(allDescrip) + 
  geom_histogram(aes(scaredSumParent, fill = Cohort), bins = 9) +
  geom_vline(xintercept = 25, lty = 2) +
  facet_wrap('Cohort', scales = 'free_y') + 
  scale_color_brewer(palette = 'Set1') +
  scale_fill_brewer(palette = 'Set1') +
  theme(legend.position = 'none') +
  labs(x = '', title = 'B', subtitle = 'Parent Report Total SCARED Score', y = 'Count') +
  theme(panel.grid.minor = element_blank(), panel.grid.major.y = element_blank())

# combine and save
histGrid = plot_grid(giHist, scaredPHist, ncol=1)
save_plot(filename = '../plots/suppHistogramsScaredpGI.pdf', histGrid)
```

# Age plot

```{r}
ageCorsGI = ggplot(allDescrip, aes(x = Age, y = cbclGISum, color = Cohort)) +
  stat_smooth(method = 'lm') +
  stat_cor(method = 'spearman',  aes(label = paste(..r.label.., ..rr.label.., ..p.label.., sep = "~`,`~"))) +
  scale_color_brewer(palette = 'Set1') +
  scale_fill_brewer(palette = 'Set1') +
  labs(y = 'CBCL GI Sum Score', subtitle ='Correlations between age and GI symptoms', title = 'A') +
  theme(legend.position = 'none')

ageCorsGI

ageCorsScaredP = ggplot(allDescrip, aes(x = Age, y = scaredSumParent, color = Cohort)) +
  geom_hline(yintercept = 25, lty = 2) +
  stat_smooth(method = 'lm', aes(fill = Cohort), lwd = 1) +
  stat_cor(method = 'spearman',  aes(label = paste(..r.label.., ..rr.label.., ..p.label.., sep = "~`,`~")),show.legend = FALSE) +
  scale_color_brewer(palette = 'Set1') +
  scale_fill_brewer(palette = 'Set1') +
  labs(y = 'Parent Report Total SCARED Score', subtitle ='Correlations between age and SCARED-P', title = 'B')

ageCorsScaredP

# combine and save
agePlot = plot_grid(ageCorsGI, ageCorsScaredP, ncol=2, align="h", rel_widths = c(1,1.4))
save_plot(filename = '../plots/suppAgeCorsPlot.pdf', plot = agePlot, base_width = 8)
```


# Sex differences plots
```{r}
allDescrip= mutate(allDescrip, sexCode = ifelse(Sex == 0, 'Male', 'Female'),
                   eca = ifelse(pi ==1,'ECA', 'Comparison'))

sexGI = ggplot(allDescrip, aes(x = sexCode, y = cbclGISum, color = Cohort)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap('Cohort') +
  theme(panel.grid.minor = element_blank()) +
  labs(x = '', y = 'CBCL GI Sum Score', title = 'A') +
  scale_color_brewer(palette = 'Set1') +
  theme(legend.position = 'none', axis.text.x = element_text(angle = 45, hjust = 1)) 

sexScaredP = ggplot(allDescrip, aes(x = sexCode, y = scaredSumParent, color = Cohort)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap('Cohort') +
  theme(panel.grid.minor = element_blank()) +
  labs(x = '', y = 'Parent Report Total SCARED Score', title = 'B') +
  scale_color_brewer(palette = 'Set1') +
  theme(legend.position = 'none', axis.text.x = element_text(angle = 45, hjust = 1)) 

# combine and save
sexPlot = plot_grid(sexGI, sexScaredP, ncol=2, align="h")
save_plot(filename = '../plots/suppSexDifferencesPlot.pdf', plot = sexPlot, base_width = 8)
```
# Sex models
```{r, results='hide'}
# GI symptoms as a function of sex
sexModGIElfk = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'NYC'), cbclGISum ~ Sex)
sexModGISB = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'LA'), cbclGISum ~ Sex)
sexModGIHBN = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'HBN'), cbclGISum ~ Sex)

# SCARED-P as a function of sex
sexModScaredPElfk = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'NYC'), scaredSumParent ~ Sex)
sexModScaredPSB = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'LA'), scaredSumParent ~ Sex)
sexModScaredPHBN = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'HBN'), scaredSumParent ~ Sex)

save(sexModGIElfk, sexModGISB, sexModGIHBN, sexModScaredPElfk, sexModScaredPSB, sexModScaredPHBN, file = '../output/sexDifferencesModelsAcrossCohorts.rda')
```

# Sex plots for SCARED-C and KDSADS in HBN
```{r}
sexScaredC = ggplot(dplyr::filter(allDescrip, Cohort == 'HBN'), aes(x = sexCode, y = scaredSumChild, color = Cohort)) +
  stat_summary(fun.data = "mean_cl_boot") +
  theme(panel.grid.minor = element_blank()) +
  labs(x = '', y = 'Child Report Total SCARED Score', title = 'C') +
  scale_color_brewer(palette = 'Set1') +
  theme(legend.position = 'none', axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap('Cohort') 

# reformat data for ksads sex differences (proportion with diagnosis)
sexKsads = dplyr::filter(allDescrip, Cohort == 'HBN', !is.na(ksadsBin)) %>%
  group_by(sexCode) %>%
  summarise(prop = sum(ksadsBin)/n(),
            n = n(),
            se = sqrt(prop*(1-prop)/n),
            Cohort = Cohort[1])

sexKsadsPlot = ggplot(sexKsads, aes(x = sexCode, y = prop, color = Cohort)) +
  geom_point() +
  geom_errorbar(aes(ymin = prop - 2*se, ymax = prop+2*se), width = 0) +
  scale_color_brewer(palette = 'Set1') +
  theme(legend.position = 'none', axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = 'P(Ksads Diagnosis)', title = 'D', x = '') +
  facet_wrap('Cohort') 


sexKsadsPlot
sexScaredC
```

## Save plots out as 1 big grid
```{r}
pdf('../plots/suppSexDifferencesChildClinician.pdf', width = 8, height = 4)
gridExtra::grid.arrange(sexGI, sexScaredP, sexScaredC,sexKsadsPlot, ncol = 4, widths = c(1.7, 1.7, 1,1))
dev.off()
```

# ECA Plots

GI and anxiety symptoms as a function of ECA in LA/NYC cohorts

```{r}
ecaGI = ggplot(dplyr::filter(allDescrip, Cohort != 'HBN'), aes(x = eca, y = cbclGISum, color = Cohort)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap('Cohort') +
  theme(panel.grid.minor = element_blank()) +
  labs(x = '', y = 'CBCL GI Sum Score', title = 'B', subtitle = 'GI symptoms') +
  scale_color_manual(values = c('#377eb8','#4daf4a')) +
  theme(legend.position = 'none')


ecaScaredP = ggplot(dplyr::filter(allDescrip, Cohort != 'HBN'), aes(x = eca, y = scaredSumParent, color = Cohort)) +
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap('Cohort') +
  theme(panel.grid.minor = element_blank()) +
  labs(x = '', y = 'Parent Report Total SCARED Score', title = 'B', subtitle = ' SCARED-P') +
  scale_color_manual(values = c('#377eb8','#4daf4a')) +
  theme(legend.position = 'none')


# combine and save
ecaPlot = plot_grid(ecaGI, ecaScaredP, ncol=2, align="h")
save_plot(filename = '../plots/suppECAPlot.pdf', plot = ecaPlot, base_width = 8)
```

# ECA models
```{r, results='hide'}
ecaModGIElfk = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'NYC'), cbclGISum ~ eca)
ecaModGISB = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'LA'), cbclGISum ~ eca)

ecaModScaredPElfk = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'NYC'), scaredSumParent ~ eca)
ecaModScaredPSB = stan_glm(data = dplyr::filter(allDescrip, Cohort == 'LA'), scaredSumParent ~ eca)

# save out models
save(ecaModGIElfk, ecaModGISB, ecaModScaredPElfk, ecaModScaredPSB, file = '../output/ecaDifferencesModelsAcrossCohorts.rda')
```

# Session Info
```{r}
sessionInfo()
```